### 2016-03-02 doc/paper.tex
the initial draft of the paper

\documentclass[conference, 10pt, twocolumn]{ieeeconf}

\IEEEoverridecommandlockouts
\overrideIEEEmargins

\usepackage[usenames]{color}
\usepackage{enumerate}
\usepackage{url}
\usepackage{subfigure}
\usepackage{amsfonts,mathrsfs}
\usepackage{amssymb,amsmath}
\usepackage{verbatim}
\usepackage{acronym}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{bbm}

%\newcommand{\remove}[1]{}
%\def\jnt#1{{{\bf #1}}}
\def\rasoul#1{{\color{blue}#1}}
%\long\def\red#1{{{\color{red}#1}}}
\def\an#1{{{\bf \color{red}#1}}}
\def\fskip#1{}

\newcounter{note}
\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}{Lemma}
\newtheorem{notation}[note]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newtheorem{acknowledgement}{Acknowledgement}

%\textwidth 6.2in \textheight 9in \setlength{\topmargin}{-0.3in}
%\setlength{\oddsidemargin}{0.1in} \setlength{\evensidemargin}{0.1in}
%\renewcommand{\theequation}{\thesection.\arabic{equation}}
\renewcommand{\theenumi}{\arabic{enumi}}
\newcommand{\qed}{\ \ {\bf q.e.d.}}

\def\1{{\bf 1}}
\def\al{\alpha}
\def\E{\mathcal{E}}
\def\Eb{\overline{\E}}
\def\L{\mathcal{L}}
\def\A{\mathcal{A}}
\def\Ps{P_{\sigma}}
\def\e{{\bf e}}
\def\ei{{\e^{(i)}}}
\def\ej{{\e^{(j)}}}
\def\ek{{\e^{(k)}}}
\def\B{{\mathcal B}}
\def\Pm{{\mathcal P}}
\def\Gb{\overline{G}}
\def\N{\mathbb{N}}
\def\F{\mathscr{F}}
\def\Finf{\mathscr{F}^{\infty}}

\def\ol{\bar}
\def\Rd{\mathbb{R}^d}
\def\l{\lambda}
\def\b{\beta}
\def\d{\delta}
\def\e{\epsilon}
\def\g{\gamma}
\def\a{\alpha}
\def\N{\mathcal{N}}
\def\s{\sigma}
\def\tl{\tilde}
\def\k{\kappa}
\def\o{\omega}
\def\rn{\mathbb{R}^n}

\def\R{\mathbb{R}}
\def\re{\mathbb{R}}
\def\gr{\nabla}
\def\cone{{\rm cone}}
\def\dist{{\rm dist}}
\def\t{\tau}
\def\qed{\ {\bf Q.E.D.}}
\def\S{\mathscr{S}}
\def\bS{\mathbb{S}}
\def\cS{\mathcal{S}}
\def\I{\mathscr{I}}
\def\Z{\mathbb{Z}}

\newcommand{\EXP}[1]{\mathsf{E}\!\left[#1\right] }
\newcommand{\prob}[1]{\mathsf{Pr}\left( #1 \right)}
\newcommand{\remove}[1]{}
\newcommand{\Rm}{\mathbb{R}^m}
\newcommand{\lra}{\leftrightarrow}
\newcommand{\lrA}{\Leftrightarrow}
\newcommand{\M}{\mathscr{M}_2}
\newcommand{\diag}{\mbox{diag}}
\newcommand{\Ginf}{G^{\infty}}
\newcommand{\Einf}{\mathscr{E}^{\inf}}
\newcommand{\tw}{\tilde{W}}
\newcommand{\xc}{\{x(k)\}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
\framebox{\begin{minipage}[c]{0.9 \columnwidth} \tt #1
\end{minipage}}\vspace{5 mm}\par}

\def\argmin{\mathop{\rm argmin}}
\def\an #1{{\color{red} #1}}

\begin{document}
\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
Replication Games}
\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
  \authorblockA{}
\thanks{\textdagger Seyed Nematollah Ahmadian is with
Coordinated Science Laboratory,
Department of Electrical and Computer Engineering,
University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
E-mail: {ahmadya2}@illinois.edu}
\thanks{
\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
Department of Electrical Engineering,
Princeton University, NJ, 08644;
E-mail: etesami,poor@Princeton.EDU}
}
\maketitle
\begin{abstract}
In this paper we consider a resource allocation
game with limited capacities over large scale networks and
propose a novel randomized algorithm for searching its purestrategy
Nash equilibrium points. It is known that such games
always admit a pure-strategy Nash equilibrium and benefit
from having a low price of anarchy. However, the best
theoretical results only provide a quasi-polynomial constant
approximation algorithm of the equilibrium points over general
networks. Here, we search the state space of the resource
allocation game for its equilibrium points. We use a random
tree based search methods to minimize a proper objective
function and direct the search toward the pure-strategy Nash
equilibrium points of the system. Through empirical results, we
demonstrate that in comparison to the best known theoretical
bounds, our technique is more efficient.
\end{abstract}
\begin{keywords}
Capacitated selfish replication game; pure Nash equilibrium (NE); Random tree algorithm.
\end{keywords}

\section{Introduction}
In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering. In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks. Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.

Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue. In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}. Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.

Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}. Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem. However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games. In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.

Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph. Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost. Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources. However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands. The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}. Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
equally interested in some objects.

In this paper, we consider the capacitated selfish replication game with binary preferences. In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs. Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions. It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium. This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5. However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium. In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.

The paper is organized as follows. In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks. We review some salient properties of such games and include some relevant existing results on this problem. In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases. Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective. We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.

\textbf{Notations}: 
For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$. For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$. We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$. For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$. The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$. Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$. We denote a specific Nash equilibrium by $P^*$. Finally, we use $|S|$ to denote the cardinality of a finite set $S$.

\section{Problem Formulation and Existing Results}\label{sec:game-model}

In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}. In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.

\subsection{CSR Game Model}
We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$. We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$. For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache. All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below). Moreover, we assume that each node has access to all the resources. For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
\begin{align}\label{eq:CSR-cost-formulation}
C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
\end{align}
where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$. Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$. Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network. We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity. In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.

\begin{figure}[htb]
\vspace{-1.5cm}
\begin{center}
\includegraphics[totalheight=.22\textheight,
width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
\end{center}
\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
\label{fig:example-model}
\end{figure}
\vspace{-0.3cm}
\begin{remark}
If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$. Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network. In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$. 
\end{remark}

\begin{remark}\label{rem:varying-cache}
Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
\end{remark}

\begin{remark}\label{rem:cost-to-radius}
Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$. This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed. 
\end{remark}

It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely

\smallskip
\begin{theorem}\label{thm:existence-NE}
The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
\end{theorem}

Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$). Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.

\section{Characterization of NE v.s Randomization}\label{sec:main-I}

In this section we first characterize the equilibrium points of the CSR game as maximizers of a proper function. Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values. The explicit form of this function and some of its properties has been given in the following lemma:

\smallskip
\begin{lemma}\label{lem:NE-characterization}
Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$. Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game. 
\end{lemma} 
\begin{proof}
For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$. In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}). But this is in contradiction with $P^*$ being an equilibrium. Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$. Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$). On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$. Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.  
\end{proof}

\smallskip
Using Lemma \ref{lem:NE-characterization}, the problem of finding NE of the system reduces to finding the maximizers of the function $f(\cdot)$. In other words, if we have an efficient algorithm which can find the global maximum of $f(\cdot)$, then we will be able to find the equilibrium points of the system efficiently. Note that here $f(\cdot)$ is not a potential function of the game, however, it can be used to drive the search process to an equilibrium. In the following theorem we show that randomization can be quite useful for maximizing such function when the players' neighborhoods are not saturated with many resources.

\smallskip
\begin{theorem}\label{thm:randomization}
Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
\end{theorem}
\begin{proof}  
Let us consider an arbitrary player $i$ such that $M_i(t)\leq \sqrt{|O|}$, and let him uniformly and independently update to one of the possible $|O|$ resources, each with probability $\frac{1}{|O|}$. We compute the expected amount of $\mathbb{E}[f(t+1)]$. For this purpose we first consider the expected change in $\mathbb{E}[M_i(t+1)]$:  
\begin{align}\nonumber
\mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
\end{align}
where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.

Next for any other node $j$ such that $i\in B(j, r_j(t)), j\neq i$ we can write
\begin{align}\nonumber
\mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
\end{align}
where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$. Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$). Therefore, we can write
\begin{align}\nonumber
&\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr 
&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
\end{align}
where the last two inequalities is due to the fact that $M_i(t)\leq \sqrt{|O|}, \forall i$. Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$. In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
\end{proof}

In fact, Theorem \ref{thm:randomization} guarantees a good improvement in the value of the objective function $f$ as long as there are not too many resources around each player. However, when the system gets closer to its equilibrium points, the speed of progress can be much slower, or there may exist a possibility where the objective function gets stuck in one of its local maximums. To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.

\section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}

\section{Conclusion}\label{sec:conclusion}
In this paper, we have studied the binary-preference capacitated selfish replication (CSR) game over general networks. We have characterized the equilibrium points of the system using a proper objective function. We leveraged this objective function and proposed a randomized algorithm based on the random tree search to find the global maximizers of this function, and hence, the NE points of the system. As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.

\bibliographystyle{IEEEtran}
\bibliography{thesisrefs}
\end{document}

### 2016-03-02 doc/abstract.tex
breaking down the paper

--- 2016-03-02 doc/paper.tex
@@
-\documentclass[conference, 10pt, twocolumn]{ieeeconf}
-
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
-
-\usepackage[usenames]{color}
-\usepackage{enumerate}
-\usepackage{url}
-\usepackage{subfigure}
-\usepackage{amsfonts,mathrsfs}
-\usepackage{amssymb,amsmath}
-\usepackage{verbatim}
-\usepackage{acronym}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{bbm}
-
-%\newcommand{\remove}[1]{}
-%\def\jnt#1{{{\bf #1}}}
-\def\rasoul#1{{\color{blue}#1}}
-%\long\def\red#1{{{\color{red}#1}}}
-\def\an#1{{{\bf \color{red}#1}}}
-\def\fskip#1{}
-
-\newcounter{note}
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}{Lemma}
-\newtheorem{notation}[note]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newtheorem{acknowledgement}{Acknowledgement}
-
-%\textwidth 6.2in \textheight 9in \setlength{\topmargin}{-0.3in}
-%\setlength{\oddsidemargin}{0.1in} \setlength{\evensidemargin}{0.1in}
-%\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\renewcommand{\theenumi}{\arabic{enumi}}
-\newcommand{\qed}{\ \ {\bf q.e.d.}}
-
-\def\1{{\bf 1}}
-\def\al{\alpha}
-\def\E{\mathcal{E}}
-\def\Eb{\overline{\E}}
-\def\L{\mathcal{L}}
-\def\A{\mathcal{A}}
-\def\Ps{P_{\sigma}}
-\def\e{{\bf e}}
-\def\ei{{\e^{(i)}}}
-\def\ej{{\e^{(j)}}}
-\def\ek{{\e^{(k)}}}
-\def\B{{\mathcal B}}
-\def\Pm{{\mathcal P}}
-\def\Gb{\overline{G}}
-\def\N{\mathbb{N}}
-\def\F{\mathscr{F}}
-\def\Finf{\mathscr{F}^{\infty}}
-
-\def\ol{\bar}
-\def\Rd{\mathbb{R}^d}
-\def\l{\lambda}
-\def\b{\beta}
-\def\d{\delta}
-\def\e{\epsilon}
-\def\g{\gamma}
-\def\a{\alpha}
-\def\N{\mathcal{N}}
-\def\s{\sigma}
-\def\tl{\tilde}
-\def\k{\kappa}
-\def\o{\omega}
-\def\rn{\mathbb{R}^n}
-
-\def\R{\mathbb{R}}
-\def\re{\mathbb{R}}
-\def\gr{\nabla}
-\def\cone{{\rm cone}}
-\def\dist{{\rm dist}}
-\def\t{\tau}
-\def\qed{\ {\bf Q.E.D.}}
-\def\S{\mathscr{S}}
-\def\bS{\mathbb{S}}
-\def\cS{\mathcal{S}}
-\def\I{\mathscr{I}}
-\def\Z{\mathbb{Z}}
-
-\newcommand{\EXP}[1]{\mathsf{E}\!\left[#1\right] }
-\newcommand{\prob}[1]{\mathsf{Pr}\left( #1 \right)}
-\newcommand{\remove}[1]{}
-\newcommand{\Rm}{\mathbb{R}^m}
-\newcommand{\lra}{\leftrightarrow}
-\newcommand{\lrA}{\Leftrightarrow}
-\newcommand{\M}{\mathscr{M}_2}
-\newcommand{\diag}{\mbox{diag}}
-\newcommand{\Ginf}{G^{\infty}}
-\newcommand{\Einf}{\mathscr{E}^{\inf}}
-\newcommand{\tw}{\tilde{W}}
-\newcommand{\xc}{\{x(k)\}}
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.9 \columnwidth} \tt #1
-\end{minipage}}\vspace{5 mm}\par}
-
-\def\argmin{\mathop{\rm argmin}}
-\def\an #1{{\color{red} #1}}
-
-\begin{document}
-\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
-Replication Games}
-\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
-  \authorblockA{}
-\thanks{\textdagger Seyed Nematollah Ahmadian is with
-Coordinated Science Laboratory,
-Department of Electrical and Computer Engineering,
-University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
-E-mail: {ahmadya2}@illinois.edu}
-\thanks{
-\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
-Department of Electrical Engineering,
-Princeton University, NJ, 08644;
-E-mail: etesami,poor@Princeton.EDU}
-}
-\maketitle
 \begin{abstract}
@@
 \end{keywords}
-
-\section{Introduction}
-In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering.
-In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks.
-Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.
-
-Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue.
-In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}.
-Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.
-
-Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}.
-Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem.
-However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games.
-In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.
-
-Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
-Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost.
-Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources.
-However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands.
-The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
-
-In this paper, we consider the capacitated selfish replication game with binary preferences.
-In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
-Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions.
-It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium.
-This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5.
-However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium.
-In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.
-
-The paper is organized as follows.
-In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks.
-We review some salient properties of such games and include some relevant existing results on this problem.
-In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
-We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
-
-\textbf{Notations}: 
-For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$.
-For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$.
-We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$.
-For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$.
-The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$.
-Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
-We denote a specific Nash equilibrium by $P^*$.
-Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
-
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
-
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
-
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
-\begin{align}\label{eq:CSR-cost-formulation}
-C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
-\end{align}
-where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
-
-\begin{figure}[htb]
-\vspace{-1.5cm}
-\begin{center}
-\includegraphics[totalheight=.22\textheight,
-width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
-\end{center}
-\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
-\label{fig:example-model}
-\end{figure}
-\vspace{-0.3cm}
-\begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
-Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
-In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
-\end{remark}
-
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
-
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
-
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
-
-\smallskip
-\begin{theorem}\label{thm:existence-NE}
-The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
-\end{theorem}
-
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
-Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.
-
-\section{Characterization of NE v.s Randomization}\label{sec:main-I}
-
-In this section we first characterize the equilibrium points of the CSR game as maximizers of a proper function.
-Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values.
-The explicit form of this function and some of its properties has been given in the following lemma:
-
-\smallskip
-\begin{lemma}\label{lem:NE-characterization}
-Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$.
-Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game.
-\end{lemma} 
-\begin{proof}
-For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
-In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}).
-But this is in contradiction with $P^*$ being an equilibrium.
-Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$.
-Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
-On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
-Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.
-\end{proof}
-
-\smallskip
-Using Lemma \ref{lem:NE-characterization}, the problem of finding NE of the system reduces to finding the maximizers of the function $f(\cdot)$.
-In other words, if we have an efficient algorithm which can find the global maximum of $f(\cdot)$, then we will be able to find the equilibrium points of the system efficiently.
-Note that here $f(\cdot)$ is not a potential function of the game, however, it can be used to drive the search process to an equilibrium.
-In the following theorem we show that randomization can be quite useful for maximizing such function when the players' neighborhoods are not saturated with many resources.
-
-\smallskip
-\begin{theorem}\label{thm:randomization}
-Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
-\end{theorem}
-\begin{proof}  
-Let us consider an arbitrary player $i$ such that $M_i(t)\leq \sqrt{|O|}$, and let him uniformly and independently update to one of the possible $|O|$ resources, each with probability $\frac{1}{|O|}$.
-We compute the expected amount of $\mathbb{E}[f(t+1)]$.
-For this purpose we first consider the expected change in $\mathbb{E}[M_i(t+1)]$:
-\begin{align}\nonumber
-\mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
-&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
-\end{align}
-where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
-
-Next for any other node $j$ such that $i\in B(j, r_j(t)), j\neq i$ we can write
-\begin{align}\nonumber
-\mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
-&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
-\end{align}
-where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
-Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$).
-Therefore, we can write
-\begin{align}\nonumber
-&\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
-&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
-\end{align}
-where the last two inequalities is due to the fact that $M_i(t)\leq \sqrt{|O|}, \forall i$.
-Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$.
-In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
-\end{proof}
-
-In fact, Theorem \ref{thm:randomization} guarantees a good improvement in the value of the objective function $f$ as long as there are not too many resources around each player.
-However, when the system gets closer to its equilibrium points, the speed of progress can be much slower, or there may exist a possibility where the objective function gets stuck in one of its local maximums.
-To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.
-
-\section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
-
-\section{Conclusion}\label{sec:conclusion}
-In this paper, we have studied the binary-preference capacitated selfish replication (CSR) game over general networks.
-We have characterized the equilibrium points of the system using a proper objective function.
-We leveraged this objective function and proposed a randomized algorithm based on the random tree search to find the global maximizers of this function, and hence, the NE points of the system.
-As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.
-
-\bibliographystyle{IEEEtran}
-\bibliography{thesisrefs}
-\end{document}

### 2016-03-02 doc/algorithm.tex
breaking down the paper

--- 2016-03-02 doc/paper.tex
@@
-\documentclass[conference, 10pt, twocolumn]{ieeeconf}
-
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
-
-\usepackage[usenames]{color}
-\usepackage{enumerate}
-\usepackage{url}
-\usepackage{subfigure}
-\usepackage{amsfonts,mathrsfs}
-\usepackage{amssymb,amsmath}
-\usepackage{verbatim}
-\usepackage{acronym}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{bbm}
-
-%\newcommand{\remove}[1]{}
-%\def\jnt#1{{{\bf #1}}}
-\def\rasoul#1{{\color{blue}#1}}
-%\long\def\red#1{{{\color{red}#1}}}
-\def\an#1{{{\bf \color{red}#1}}}
-\def\fskip#1{}
-
-\newcounter{note}
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}{Lemma}
-\newtheorem{notation}[note]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newtheorem{acknowledgement}{Acknowledgement}
-
-%\textwidth 6.2in \textheight 9in \setlength{\topmargin}{-0.3in}
-%\setlength{\oddsidemargin}{0.1in} \setlength{\evensidemargin}{0.1in}
-%\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\renewcommand{\theenumi}{\arabic{enumi}}
-\newcommand{\qed}{\ \ {\bf q.e.d.}}
-
-\def\1{{\bf 1}}
-\def\al{\alpha}
-\def\E{\mathcal{E}}
-\def\Eb{\overline{\E}}
-\def\L{\mathcal{L}}
-\def\A{\mathcal{A}}
-\def\Ps{P_{\sigma}}
-\def\e{{\bf e}}
-\def\ei{{\e^{(i)}}}
-\def\ej{{\e^{(j)}}}
-\def\ek{{\e^{(k)}}}
-\def\B{{\mathcal B}}
-\def\Pm{{\mathcal P}}
-\def\Gb{\overline{G}}
-\def\N{\mathbb{N}}
-\def\F{\mathscr{F}}
-\def\Finf{\mathscr{F}^{\infty}}
-
-\def\ol{\bar}
-\def\Rd{\mathbb{R}^d}
-\def\l{\lambda}
-\def\b{\beta}
-\def\d{\delta}
-\def\e{\epsilon}
-\def\g{\gamma}
-\def\a{\alpha}
-\def\N{\mathcal{N}}
-\def\s{\sigma}
-\def\tl{\tilde}
-\def\k{\kappa}
-\def\o{\omega}
-\def\rn{\mathbb{R}^n}
-
-\def\R{\mathbb{R}}
-\def\re{\mathbb{R}}
-\def\gr{\nabla}
-\def\cone{{\rm cone}}
-\def\dist{{\rm dist}}
-\def\t{\tau}
-\def\qed{\ {\bf Q.E.D.}}
-\def\S{\mathscr{S}}
-\def\bS{\mathbb{S}}
-\def\cS{\mathcal{S}}
-\def\I{\mathscr{I}}
-\def\Z{\mathbb{Z}}
-
-\newcommand{\EXP}[1]{\mathsf{E}\!\left[#1\right] }
-\newcommand{\prob}[1]{\mathsf{Pr}\left( #1 \right)}
-\newcommand{\remove}[1]{}
-\newcommand{\Rm}{\mathbb{R}^m}
-\newcommand{\lra}{\leftrightarrow}
-\newcommand{\lrA}{\Leftrightarrow}
-\newcommand{\M}{\mathscr{M}_2}
-\newcommand{\diag}{\mbox{diag}}
-\newcommand{\Ginf}{G^{\infty}}
-\newcommand{\Einf}{\mathscr{E}^{\inf}}
-\newcommand{\tw}{\tilde{W}}
-\newcommand{\xc}{\{x(k)\}}
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.9 \columnwidth} \tt #1
-\end{minipage}}\vspace{5 mm}\par}
-
-\def\argmin{\mathop{\rm argmin}}
-\def\an #1{{\color{red} #1}}
-
-\begin{document}
-\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
-Replication Games}
-\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
-  \authorblockA{}
-\thanks{\textdagger Seyed Nematollah Ahmadian is with
-Coordinated Science Laboratory,
-Department of Electrical and Computer Engineering,
-University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
-E-mail: {ahmadya2}@illinois.edu}
-\thanks{
-\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
-Department of Electrical Engineering,
-Princeton University, NJ, 08644;
-E-mail: etesami,poor@Princeton.EDU}
-}
-\maketitle
-\begin{abstract}
-In this paper we consider a resource allocation
-game with limited capacities over large scale networks and
-propose a novel randomized algorithm for searching its purestrategy
-Nash equilibrium points. It is known that such games
-always admit a pure-strategy Nash equilibrium and benefit
-from having a low price of anarchy. However, the best
-theoretical results only provide a quasi-polynomial constant
-approximation algorithm of the equilibrium points over general
-networks. Here, we search the state space of the resource
-allocation game for its equilibrium points. We use a random
-tree based search methods to minimize a proper objective
-function and direct the search toward the pure-strategy Nash
-equilibrium points of the system. Through empirical results, we
-demonstrate that in comparison to the best known theoretical
-bounds, our technique is more efficient.
-\end{abstract}
-\begin{keywords}
-Capacitated selfish replication game; pure Nash equilibrium (NE); Random tree algorithm.
-\end{keywords}
-
-\section{Introduction}
-In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering.
-In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks.
-Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.
-
-Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue.
-In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}.
-Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.
-
-Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}.
-Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem.
-However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games.
-In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.
-
-Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
-Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost.
-Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources.
-However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands.
-The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
-
-In this paper, we consider the capacitated selfish replication game with binary preferences.
-In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
-Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions.
-It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium.
-This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5.
-However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium.
-In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.
-
-The paper is organized as follows.
-In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks.
-We review some salient properties of such games and include some relevant existing results on this problem.
-In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
-We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
-
-\textbf{Notations}: 
-For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$.
-For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$.
-We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$.
-For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$.
-The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$.
-Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
-We denote a specific Nash equilibrium by $P^*$.
-Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
-
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
-
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
-
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
-\begin{align}\label{eq:CSR-cost-formulation}
-C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
-\end{align}
-where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
-
-\begin{figure}[htb]
-\vspace{-1.5cm}
-\begin{center}
-\includegraphics[totalheight=.22\textheight,
-width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
-\end{center}
-\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
-\label{fig:example-model}
-\end{figure}
-\vspace{-0.3cm}
-\begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
-Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
-In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
-\end{remark}
-
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
-
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
-
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
-
-\smallskip
-\begin{theorem}\label{thm:existence-NE}
-The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
-\end{theorem}
-
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
-Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.
-
-\section{Characterization of NE v.s Randomization}\label{sec:main-I}
-
-In this section we first characterize the equilibrium points of the CSR game as maximizers of a proper function.
-Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values.
-The explicit form of this function and some of its properties has been given in the following lemma:
-
-\smallskip
-\begin{lemma}\label{lem:NE-characterization}
-Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$.
-Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game.
-\end{lemma} 
-\begin{proof}
-For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
-In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}).
-But this is in contradiction with $P^*$ being an equilibrium.
-Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$.
-Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
-On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
-Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.
-\end{proof}
-
-\smallskip
-Using Lemma \ref{lem:NE-characterization}, the problem of finding NE of the system reduces to finding the maximizers of the function $f(\cdot)$.
-In other words, if we have an efficient algorithm which can find the global maximum of $f(\cdot)$, then we will be able to find the equilibrium points of the system efficiently.
-Note that here $f(\cdot)$ is not a potential function of the game, however, it can be used to drive the search process to an equilibrium.
-In the following theorem we show that randomization can be quite useful for maximizing such function when the players' neighborhoods are not saturated with many resources.
-
-\smallskip
-\begin{theorem}\label{thm:randomization}
-Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
-\end{theorem}
-\begin{proof}  
-Let us consider an arbitrary player $i$ such that $M_i(t)\leq \sqrt{|O|}$, and let him uniformly and independently update to one of the possible $|O|$ resources, each with probability $\frac{1}{|O|}$.
-We compute the expected amount of $\mathbb{E}[f(t+1)]$.
-For this purpose we first consider the expected change in $\mathbb{E}[M_i(t+1)]$:
-\begin{align}\nonumber
-\mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
-&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
-\end{align}
-where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
-
-Next for any other node $j$ such that $i\in B(j, r_j(t)), j\neq i$ we can write
-\begin{align}\nonumber
-\mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
-&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
-\end{align}
-where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
-Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$).
-Therefore, we can write
-\begin{align}\nonumber
-&\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
-&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
-\end{align}
-where the last two inequalities is due to the fact that $M_i(t)\leq \sqrt{|O|}, \forall i$.
-Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$.
-In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
-\end{proof}
-
-In fact, Theorem \ref{thm:randomization} guarantees a good improvement in the value of the objective function $f$ as long as there are not too many resources around each player.
-However, when the system gets closer to its equilibrium points, the speed of progress can be much slower, or there may exist a possibility where the objective function gets stuck in one of its local maximums.
-To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.
-
 \section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
-
-\section{Conclusion}\label{sec:conclusion}
-In this paper, we have studied the binary-preference capacitated selfish replication (CSR) game over general networks.
-We have characterized the equilibrium points of the system using a proper objective function.
-We leveraged this objective function and proposed a randomized algorithm based on the random tree search to find the global maximizers of this function, and hence, the NE points of the system.
-As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.
-
-\bibliographystyle{IEEEtran}
-\bibliography{thesisrefs}
-\end{document}

### 2016-03-02 doc/conclusion.tex
breaking down the paper

--- 2016-03-02 doc/paper.tex
@@
-\documentclass[conference, 10pt, twocolumn]{ieeeconf}
-
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
-
-\usepackage[usenames]{color}
-\usepackage{enumerate}
-\usepackage{url}
-\usepackage{subfigure}
-\usepackage{amsfonts,mathrsfs}
-\usepackage{amssymb,amsmath}
-\usepackage{verbatim}
-\usepackage{acronym}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{bbm}
-
-%\newcommand{\remove}[1]{}
-%\def\jnt#1{{{\bf #1}}}
-\def\rasoul#1{{\color{blue}#1}}
-%\long\def\red#1{{{\color{red}#1}}}
-\def\an#1{{{\bf \color{red}#1}}}
-\def\fskip#1{}
-
-\newcounter{note}
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}{Lemma}
-\newtheorem{notation}[note]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newtheorem{acknowledgement}{Acknowledgement}
-
-%\textwidth 6.2in \textheight 9in \setlength{\topmargin}{-0.3in}
-%\setlength{\oddsidemargin}{0.1in} \setlength{\evensidemargin}{0.1in}
-%\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\renewcommand{\theenumi}{\arabic{enumi}}
-\newcommand{\qed}{\ \ {\bf q.e.d.}}
-
-\def\1{{\bf 1}}
-\def\al{\alpha}
-\def\E{\mathcal{E}}
-\def\Eb{\overline{\E}}
-\def\L{\mathcal{L}}
-\def\A{\mathcal{A}}
-\def\Ps{P_{\sigma}}
-\def\e{{\bf e}}
-\def\ei{{\e^{(i)}}}
-\def\ej{{\e^{(j)}}}
-\def\ek{{\e^{(k)}}}
-\def\B{{\mathcal B}}
-\def\Pm{{\mathcal P}}
-\def\Gb{\overline{G}}
-\def\N{\mathbb{N}}
-\def\F{\mathscr{F}}
-\def\Finf{\mathscr{F}^{\infty}}
-
-\def\ol{\bar}
-\def\Rd{\mathbb{R}^d}
-\def\l{\lambda}
-\def\b{\beta}
-\def\d{\delta}
-\def\e{\epsilon}
-\def\g{\gamma}
-\def\a{\alpha}
-\def\N{\mathcal{N}}
-\def\s{\sigma}
-\def\tl{\tilde}
-\def\k{\kappa}
-\def\o{\omega}
-\def\rn{\mathbb{R}^n}
-
-\def\R{\mathbb{R}}
-\def\re{\mathbb{R}}
-\def\gr{\nabla}
-\def\cone{{\rm cone}}
-\def\dist{{\rm dist}}
-\def\t{\tau}
-\def\qed{\ {\bf Q.E.D.}}
-\def\S{\mathscr{S}}
-\def\bS{\mathbb{S}}
-\def\cS{\mathcal{S}}
-\def\I{\mathscr{I}}
-\def\Z{\mathbb{Z}}
-
-\newcommand{\EXP}[1]{\mathsf{E}\!\left[#1\right] }
-\newcommand{\prob}[1]{\mathsf{Pr}\left( #1 \right)}
-\newcommand{\remove}[1]{}
-\newcommand{\Rm}{\mathbb{R}^m}
-\newcommand{\lra}{\leftrightarrow}
-\newcommand{\lrA}{\Leftrightarrow}
-\newcommand{\M}{\mathscr{M}_2}
-\newcommand{\diag}{\mbox{diag}}
-\newcommand{\Ginf}{G^{\infty}}
-\newcommand{\Einf}{\mathscr{E}^{\inf}}
-\newcommand{\tw}{\tilde{W}}
-\newcommand{\xc}{\{x(k)\}}
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.9 \columnwidth} \tt #1
-\end{minipage}}\vspace{5 mm}\par}
-
-\def\argmin{\mathop{\rm argmin}}
-\def\an #1{{\color{red} #1}}
-
-\begin{document}
-\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
-Replication Games}
-\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
-  \authorblockA{}
-\thanks{\textdagger Seyed Nematollah Ahmadian is with
-Coordinated Science Laboratory,
-Department of Electrical and Computer Engineering,
-University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
-E-mail: {ahmadya2}@illinois.edu}
-\thanks{
-\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
-Department of Electrical Engineering,
-Princeton University, NJ, 08644;
-E-mail: etesami,poor@Princeton.EDU}
-}
-\maketitle
-\begin{abstract}
-In this paper we consider a resource allocation
-game with limited capacities over large scale networks and
-propose a novel randomized algorithm for searching its purestrategy
-Nash equilibrium points. It is known that such games
-always admit a pure-strategy Nash equilibrium and benefit
-from having a low price of anarchy. However, the best
-theoretical results only provide a quasi-polynomial constant
-approximation algorithm of the equilibrium points over general
-networks. Here, we search the state space of the resource
-allocation game for its equilibrium points. We use a random
-tree based search methods to minimize a proper objective
-function and direct the search toward the pure-strategy Nash
-equilibrium points of the system. Through empirical results, we
-demonstrate that in comparison to the best known theoretical
-bounds, our technique is more efficient.
-\end{abstract}
-\begin{keywords}
-Capacitated selfish replication game; pure Nash equilibrium (NE); Random tree algorithm.
-\end{keywords}
-
-\section{Introduction}
-In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering.
-In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks.
-Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.
-
-Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue.
-In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}.
-Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.
-
-Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}.
-Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem.
-However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games.
-In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.
-
-Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
-Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost.
-Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources.
-However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands.
-The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
-
-In this paper, we consider the capacitated selfish replication game with binary preferences.
-In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
-Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions.
-It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium.
-This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5.
-However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium.
-In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.
-
-The paper is organized as follows.
-In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks.
-We review some salient properties of such games and include some relevant existing results on this problem.
-In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
-We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
-
-\textbf{Notations}: 
-For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$.
-For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$.
-We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$.
-For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$.
-The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$.
-Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
-We denote a specific Nash equilibrium by $P^*$.
-Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
-
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
-
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
-
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
-\begin{align}\label{eq:CSR-cost-formulation}
-C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
-\end{align}
-where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
-
-\begin{figure}[htb]
-\vspace{-1.5cm}
-\begin{center}
-\includegraphics[totalheight=.22\textheight,
-width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
-\end{center}
-\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
-\label{fig:example-model}
-\end{figure}
-\vspace{-0.3cm}
-\begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
-Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
-In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
-\end{remark}
-
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
-
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
-
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
-
-\smallskip
-\begin{theorem}\label{thm:existence-NE}
-The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
-\end{theorem}
-
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
-Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.
-
-\section{Characterization of NE v.s Randomization}\label{sec:main-I}
-
-In this section we first characterize the equilibrium points of the CSR game as maximizers of a proper function.
-Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values.
-The explicit form of this function and some of its properties has been given in the following lemma:
-
-\smallskip
-\begin{lemma}\label{lem:NE-characterization}
-Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$.
-Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game.
-\end{lemma} 
-\begin{proof}
-For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
-In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}).
-But this is in contradiction with $P^*$ being an equilibrium.
-Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$.
-Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
-On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
-Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.
-\end{proof}
-
-\smallskip
-Using Lemma \ref{lem:NE-characterization}, the problem of finding NE of the system reduces to finding the maximizers of the function $f(\cdot)$.
-In other words, if we have an efficient algorithm which can find the global maximum of $f(\cdot)$, then we will be able to find the equilibrium points of the system efficiently.
-Note that here $f(\cdot)$ is not a potential function of the game, however, it can be used to drive the search process to an equilibrium.
-In the following theorem we show that randomization can be quite useful for maximizing such function when the players' neighborhoods are not saturated with many resources.
-
-\smallskip
-\begin{theorem}\label{thm:randomization}
-Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
-\end{theorem}
-\begin{proof}  
-Let us consider an arbitrary player $i$ such that $M_i(t)\leq \sqrt{|O|}$, and let him uniformly and independently update to one of the possible $|O|$ resources, each with probability $\frac{1}{|O|}$.
-We compute the expected amount of $\mathbb{E}[f(t+1)]$.
-For this purpose we first consider the expected change in $\mathbb{E}[M_i(t+1)]$:
-\begin{align}\nonumber
-\mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
-&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
-\end{align}
-where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
-
-Next for any other node $j$ such that $i\in B(j, r_j(t)), j\neq i$ we can write
-\begin{align}\nonumber
-\mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
-&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
-\end{align}
-where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
-Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$).
-Therefore, we can write
-\begin{align}\nonumber
-&\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
-&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
-\end{align}
-where the last two inequalities is due to the fact that $M_i(t)\leq \sqrt{|O|}, \forall i$.
-Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$.
-In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
-\end{proof}
-
-In fact, Theorem \ref{thm:randomization} guarantees a good improvement in the value of the objective function $f$ as long as there are not too many resources around each player.
-However, when the system gets closer to its equilibrium points, the speed of progress can be much slower, or there may exist a possibility where the objective function gets stuck in one of its local maximums.
-To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.
-
-\section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
-
 \section{Conclusion}\label{sec:conclusion}
@@
 As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.
-
-\bibliographystyle{IEEEtran}
-\bibliography{thesisrefs}
-\end{document}

### 2016-03-02 doc/introduction.tex
breaking down the paper

--- 2016-03-02 doc/paper.tex
@@
-\documentclass[conference, 10pt, twocolumn]{ieeeconf}
-
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
-
-\usepackage[usenames]{color}
-\usepackage{enumerate}
-\usepackage{url}
-\usepackage{subfigure}
-\usepackage{amsfonts,mathrsfs}
-\usepackage{amssymb,amsmath}
-\usepackage{verbatim}
-\usepackage{acronym}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{bbm}
-
-%\newcommand{\remove}[1]{}
-%\def\jnt#1{{{\bf #1}}}
-\def\rasoul#1{{\color{blue}#1}}
-%\long\def\red#1{{{\color{red}#1}}}
-\def\an#1{{{\bf \color{red}#1}}}
-\def\fskip#1{}
-
-\newcounter{note}
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}{Lemma}
-\newtheorem{notation}[note]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newtheorem{acknowledgement}{Acknowledgement}
-
-%\textwidth 6.2in \textheight 9in \setlength{\topmargin}{-0.3in}
-%\setlength{\oddsidemargin}{0.1in} \setlength{\evensidemargin}{0.1in}
-%\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\renewcommand{\theenumi}{\arabic{enumi}}
-\newcommand{\qed}{\ \ {\bf q.e.d.}}
-
-\def\1{{\bf 1}}
-\def\al{\alpha}
-\def\E{\mathcal{E}}
-\def\Eb{\overline{\E}}
-\def\L{\mathcal{L}}
-\def\A{\mathcal{A}}
-\def\Ps{P_{\sigma}}
-\def\e{{\bf e}}
-\def\ei{{\e^{(i)}}}
-\def\ej{{\e^{(j)}}}
-\def\ek{{\e^{(k)}}}
-\def\B{{\mathcal B}}
-\def\Pm{{\mathcal P}}
-\def\Gb{\overline{G}}
-\def\N{\mathbb{N}}
-\def\F{\mathscr{F}}
-\def\Finf{\mathscr{F}^{\infty}}
-
-\def\ol{\bar}
-\def\Rd{\mathbb{R}^d}
-\def\l{\lambda}
-\def\b{\beta}
-\def\d{\delta}
-\def\e{\epsilon}
-\def\g{\gamma}
-\def\a{\alpha}
-\def\N{\mathcal{N}}
-\def\s{\sigma}
-\def\tl{\tilde}
-\def\k{\kappa}
-\def\o{\omega}
-\def\rn{\mathbb{R}^n}
-
-\def\R{\mathbb{R}}
-\def\re{\mathbb{R}}
-\def\gr{\nabla}
-\def\cone{{\rm cone}}
-\def\dist{{\rm dist}}
-\def\t{\tau}
-\def\qed{\ {\bf Q.E.D.}}
-\def\S{\mathscr{S}}
-\def\bS{\mathbb{S}}
-\def\cS{\mathcal{S}}
-\def\I{\mathscr{I}}
-\def\Z{\mathbb{Z}}
-
-\newcommand{\EXP}[1]{\mathsf{E}\!\left[#1\right] }
-\newcommand{\prob}[1]{\mathsf{Pr}\left( #1 \right)}
-\newcommand{\remove}[1]{}
-\newcommand{\Rm}{\mathbb{R}^m}
-\newcommand{\lra}{\leftrightarrow}
-\newcommand{\lrA}{\Leftrightarrow}
-\newcommand{\M}{\mathscr{M}_2}
-\newcommand{\diag}{\mbox{diag}}
-\newcommand{\Ginf}{G^{\infty}}
-\newcommand{\Einf}{\mathscr{E}^{\inf}}
-\newcommand{\tw}{\tilde{W}}
-\newcommand{\xc}{\{x(k)\}}
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.9 \columnwidth} \tt #1
-\end{minipage}}\vspace{5 mm}\par}
-
-\def\argmin{\mathop{\rm argmin}}
-\def\an #1{{\color{red} #1}}
-
-\begin{document}
-\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
-Replication Games}
-\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
-  \authorblockA{}
-\thanks{\textdagger Seyed Nematollah Ahmadian is with
-Coordinated Science Laboratory,
-Department of Electrical and Computer Engineering,
-University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
-E-mail: {ahmadya2}@illinois.edu}
-\thanks{
-\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
-Department of Electrical Engineering,
-Princeton University, NJ, 08644;
-E-mail: etesami,poor@Princeton.EDU}
-}
-\maketitle
-\begin{abstract}
-In this paper we consider a resource allocation
-game with limited capacities over large scale networks and
-propose a novel randomized algorithm for searching its purestrategy
-Nash equilibrium points. It is known that such games
-always admit a pure-strategy Nash equilibrium and benefit
-from having a low price of anarchy. However, the best
-theoretical results only provide a quasi-polynomial constant
-approximation algorithm of the equilibrium points over general
-networks. Here, we search the state space of the resource
-allocation game for its equilibrium points. We use a random
-tree based search methods to minimize a proper objective
-function and direct the search toward the pure-strategy Nash
-equilibrium points of the system. Through empirical results, we
-demonstrate that in comparison to the best known theoretical
-bounds, our technique is more efficient.
-\end{abstract}
-\begin{keywords}
-Capacitated selfish replication game; pure Nash equilibrium (NE); Random tree algorithm.
-\end{keywords}
-
 \section{Introduction}
@@
 Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
-
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
-
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
-
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
-\begin{align}\label{eq:CSR-cost-formulation}
-C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
-\end{align}
-where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
-
-\begin{figure}[htb]
-\vspace{-1.5cm}
-\begin{center}
-\includegraphics[totalheight=.22\textheight,
-width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
-\end{center}
-\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
-\label{fig:example-model}
-\end{figure}
-\vspace{-0.3cm}
-\begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
-Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
-In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
-\end{remark}
-
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
-
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
-
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
-
-\smallskip
-\begin{theorem}\label{thm:existence-NE}
-The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
-\end{theorem}
-
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
-Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.
-
-\section{Characterization of NE v.s Randomization}\label{sec:main-I}
-
-In this section we first characterize the equilibrium points of the CSR game as maximizers of a proper function.
-Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values.
-The explicit form of this function and some of its properties has been given in the following lemma:
-
-\smallskip
-\begin{lemma}\label{lem:NE-characterization}
-Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$.
-Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game.
-\end{lemma} 
-\begin{proof}
-For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
-In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}).
-But this is in contradiction with $P^*$ being an equilibrium.
-Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$.
-Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
-On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
-Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.
-\end{proof}
-
-\smallskip
-Using Lemma \ref{lem:NE-characterization}, the problem of finding NE of the system reduces to finding the maximizers of the function $f(\cdot)$.
-In other words, if we have an efficient algorithm which can find the global maximum of $f(\cdot)$, then we will be able to find the equilibrium points of the system efficiently.
-Note that here $f(\cdot)$ is not a potential function of the game, however, it can be used to drive the search process to an equilibrium.
-In the following theorem we show that randomization can be quite useful for maximizing such function when the players' neighborhoods are not saturated with many resources.
-
-\smallskip
-\begin{theorem}\label{thm:randomization}
-Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
-\end{theorem}
-\begin{proof}  
-Let us consider an arbitrary player $i$ such that $M_i(t)\leq \sqrt{|O|}$, and let him uniformly and independently update to one of the possible $|O|$ resources, each with probability $\frac{1}{|O|}$.
-We compute the expected amount of $\mathbb{E}[f(t+1)]$.
-For this purpose we first consider the expected change in $\mathbb{E}[M_i(t+1)]$:
-\begin{align}\nonumber
-\mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
-&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
-\end{align}
-where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
-
-Next for any other node $j$ such that $i\in B(j, r_j(t)), j\neq i$ we can write
-\begin{align}\nonumber
-\mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
-&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
-\end{align}
-where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
-Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$).
-Therefore, we can write
-\begin{align}\nonumber
-&\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
-&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
-\end{align}
-where the last two inequalities is due to the fact that $M_i(t)\leq \sqrt{|O|}, \forall i$.
-Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$.
-In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
-\end{proof}
-
-In fact, Theorem \ref{thm:randomization} guarantees a good improvement in the value of the objective function $f$ as long as there are not too many resources around each player.
-However, when the system gets closer to its equilibrium points, the speed of progress can be much slower, or there may exist a possibility where the objective function gets stuck in one of its local maximums.
-To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.
-
-\section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
-
-\section{Conclusion}\label{sec:conclusion}
-In this paper, we have studied the binary-preference capacitated selfish replication (CSR) game over general networks.
-We have characterized the equilibrium points of the system using a proper objective function.
-We leveraged this objective function and proposed a randomized algorithm based on the random tree search to find the global maximizers of this function, and hence, the NE points of the system.
-As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.
-
-\bibliographystyle{IEEEtran}
-\bibliography{thesisrefs}
-\end{document}

### 2016-03-02 doc/motivation.tex
breaking down the paper

--- 2016-03-02 doc/paper.tex
@@
-\documentclass[conference, 10pt, twocolumn]{ieeeconf}
-
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins
-
-\usepackage[usenames]{color}
-\usepackage{enumerate}
-\usepackage{url}
-\usepackage{subfigure}
-\usepackage{amsfonts,mathrsfs}
-\usepackage{amssymb,amsmath}
-\usepackage{verbatim}
-\usepackage{acronym}
-\usepackage{mathtools}
-\usepackage{graphicx}
-\usepackage{bbm}
-
-%\newcommand{\remove}[1]{}
-%\def\jnt#1{{{\bf #1}}}
-\def\rasoul#1{{\color{blue}#1}}
-%\long\def\red#1{{{\color{red}#1}}}
-\def\an#1{{{\bf \color{red}#1}}}
-\def\fskip#1{}
-
-\newcounter{note}
-\newtheorem{theorem}{Theorem}
-\newtheorem{assumption}{Assumption}
-\newtheorem{algorithm}[theorem]{Algorithm}
-\newtheorem{axiom}[theorem]{Axiom}
-\newtheorem{case}[theorem]{Case}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{conclusion}[theorem]{Conclusion}
-\newtheorem{condition}[theorem]{Condition}
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{corollary}{Corollary}
-\newtheorem{criterion}[theorem]{Criterion}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-\newtheorem{exercise}[theorem]{Exercise}
-\newtheorem{lemma}{Lemma}
-\newtheorem{notation}[note]{Notation}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{remark}{Remark}
-\newtheorem{solution}[theorem]{Solution}
-\newtheorem{summary}[theorem]{Summary}
-\newtheorem{acknowledgement}{Acknowledgement}
-
-%\textwidth 6.2in \textheight 9in \setlength{\topmargin}{-0.3in}
-%\setlength{\oddsidemargin}{0.1in} \setlength{\evensidemargin}{0.1in}
-%\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\renewcommand{\theenumi}{\arabic{enumi}}
-\newcommand{\qed}{\ \ {\bf q.e.d.}}
-
-\def\1{{\bf 1}}
-\def\al{\alpha}
-\def\E{\mathcal{E}}
-\def\Eb{\overline{\E}}
-\def\L{\mathcal{L}}
-\def\A{\mathcal{A}}
-\def\Ps{P_{\sigma}}
-\def\e{{\bf e}}
-\def\ei{{\e^{(i)}}}
-\def\ej{{\e^{(j)}}}
-\def\ek{{\e^{(k)}}}
-\def\B{{\mathcal B}}
-\def\Pm{{\mathcal P}}
-\def\Gb{\overline{G}}
-\def\N{\mathbb{N}}
-\def\F{\mathscr{F}}
-\def\Finf{\mathscr{F}^{\infty}}
-
-\def\ol{\bar}
-\def\Rd{\mathbb{R}^d}
-\def\l{\lambda}
-\def\b{\beta}
-\def\d{\delta}
-\def\e{\epsilon}
-\def\g{\gamma}
-\def\a{\alpha}
-\def\N{\mathcal{N}}
-\def\s{\sigma}
-\def\tl{\tilde}
-\def\k{\kappa}
-\def\o{\omega}
-\def\rn{\mathbb{R}^n}
-
-\def\R{\mathbb{R}}
-\def\re{\mathbb{R}}
-\def\gr{\nabla}
-\def\cone{{\rm cone}}
-\def\dist{{\rm dist}}
-\def\t{\tau}
-\def\qed{\ {\bf Q.E.D.}}
-\def\S{\mathscr{S}}
-\def\bS{\mathbb{S}}
-\def\cS{\mathcal{S}}
-\def\I{\mathscr{I}}
-\def\Z{\mathbb{Z}}
-
-\newcommand{\EXP}[1]{\mathsf{E}\!\left[#1\right] }
-\newcommand{\prob}[1]{\mathsf{Pr}\left( #1 \right)}
-\newcommand{\remove}[1]{}
-\newcommand{\Rm}{\mathbb{R}^m}
-\newcommand{\lra}{\leftrightarrow}
-\newcommand{\lrA}{\Leftrightarrow}
-\newcommand{\M}{\mathscr{M}_2}
-\newcommand{\diag}{\mbox{diag}}
-\newcommand{\Ginf}{G^{\infty}}
-\newcommand{\Einf}{\mathscr{E}^{\inf}}
-\newcommand{\tw}{\tilde{W}}
-\newcommand{\xc}{\{x(k)\}}
-\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
-\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
-
-\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent \marginpar{\textsc{ToDo}}
-\framebox{\begin{minipage}[c]{0.9 \columnwidth} \tt #1
-\end{minipage}}\vspace{5 mm}\par}
-
-\def\argmin{\mathop{\rm argmin}}
-\def\an #1{{\color{red} #1}}
-
-\begin{document}
-\title{Random Tree Search Algorithm for Nash Equilibrium in Capacitated Selfish
-Replication Games}
-\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
-  \authorblockA{}
-\thanks{\textdagger Seyed Nematollah Ahmadian is with
-Coordinated Science Laboratory,
-Department of Electrical and Computer Engineering,
-University of Illinois at Urbana-Champaign, Urbana, IL, 61801;
-E-mail: {ahmadya2}@illinois.edu}
-\thanks{
-\textdaggerdbl Seyed Rasoul Etesami and H. Vincent Poor are with
-Department of Electrical Engineering,
-Princeton University, NJ, 08644;
-E-mail: etesami,poor@Princeton.EDU}
-}
-\maketitle
-\begin{abstract}
-In this paper we consider a resource allocation
-game with limited capacities over large scale networks and
-propose a novel randomized algorithm for searching its purestrategy
-Nash equilibrium points. It is known that such games
-always admit a pure-strategy Nash equilibrium and benefit
-from having a low price of anarchy. However, the best
-theoretical results only provide a quasi-polynomial constant
-approximation algorithm of the equilibrium points over general
-networks. Here, we search the state space of the resource
-allocation game for its equilibrium points. We use a random
-tree based search methods to minimize a proper objective
-function and direct the search toward the pure-strategy Nash
-equilibrium points of the system. Through empirical results, we
-demonstrate that in comparison to the best known theoretical
-bounds, our technique is more efficient.
-\end{abstract}
-\begin{keywords}
-Capacitated selfish replication game; pure Nash equilibrium (NE); Random tree algorithm.
-\end{keywords}
-
-\section{Introduction}
-In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering.
-In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks.
-Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.
-
-Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue.
-In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}.
-Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.
-
-Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}.
-Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem.
-However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games.
-In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.
-
-Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
-Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost.
-Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources.
-However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands.
-The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
-
-In this paper, we consider the capacitated selfish replication game with binary preferences.
-In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
-Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions.
-It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium.
-This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5.
-However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium.
-In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.
-
-The paper is organized as follows.
-In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks.
-We review some salient properties of such games and include some relevant existing results on this problem.
-In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
-We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
-
-\textbf{Notations}: 
-For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$.
-For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$.
-We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$.
-For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$.
-The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$.
-Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
-We denote a specific Nash equilibrium by $P^*$.
-Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
-
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
-
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
-
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
-\begin{align}\label{eq:CSR-cost-formulation}
-C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
-\end{align}
-where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
-
-\begin{figure}[htb]
-\vspace{-1.5cm}
-\begin{center}
-\includegraphics[totalheight=.22\textheight,
-width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
-\end{center}
-\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
-\label{fig:example-model}
-\end{figure}
-\vspace{-0.3cm}
-\begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
-Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
-In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
-\end{remark}
-
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
-
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
-
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
-
-\smallskip
-\begin{theorem}\label{thm:existence-NE}
-The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
-\end{theorem}
-
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
-Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.
-
 \section{Characterization of NE v.s Randomization}\label{sec:main-I}
@@
 To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.
-
-\section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
-
-\section{Conclusion}\label{sec:conclusion}
-In this paper, we have studied the binary-preference capacitated selfish replication (CSR) game over general networks.
-We have characterized the equilibrium points of the system using a proper objective function.
-We leveraged this objective function and proposed a randomized algorithm based on the random tree search to find the global maximizers of this function, and hence, the NE points of the system.
-As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.
-
-\bibliographystyle{IEEEtran}
-\bibliography{thesisrefs}
-\end{document}

### 2016-03-02 doc/paper.tex
breaking down the paper

@@
 \maketitle
-\begin{abstract}
-In this paper we consider a resource allocation
-game with limited capacities over large scale networks and
-propose a novel randomized algorithm for searching its purestrategy
-Nash equilibrium points. It is known that such games
-always admit a pure-strategy Nash equilibrium and benefit
-from having a low price of anarchy. However, the best
-theoretical results only provide a quasi-polynomial constant
-approximation algorithm of the equilibrium points over general
-networks. Here, we search the state space of the resource
-allocation game for its equilibrium points. We use a random
-tree based search methods to minimize a proper objective
-function and direct the search toward the pure-strategy Nash
-equilibrium points of the system. Through empirical results, we
-demonstrate that in comparison to the best known theoretical
-bounds, our technique is more efficient.
-\end{abstract}
-\begin{keywords}
-Capacitated selfish replication game; pure Nash equilibrium (NE); Random tree algorithm.
-\end{keywords}
-
-\section{Introduction}
-In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering.
-In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks.
-Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.
-
-Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue.
-In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}.
-Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.
-
-Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}.
-Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem.
-However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games.
-In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.
-
-Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
-Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost.
-Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources.
-However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands.
-The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
-
-In this paper, we consider the capacitated selfish replication game with binary preferences.
-In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
-Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions.
-It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium.
-This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5.
-However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium.
-In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.
-
-The paper is organized as follows.
-In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks.
-We review some salient properties of such games and include some relevant existing results on this problem.
-In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
-We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
-
-\textbf{Notations}: 
-For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$.
-For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$.
-We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$.
-For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$.
-The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$.
-Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
-We denote a specific Nash equilibrium by $P^*$.
-Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
-
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
-
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
-
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
-\begin{align}\label{eq:CSR-cost-formulation}
-C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)), 
-\end{align}
-where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
-
-\begin{figure}[htb]
-\vspace{-1.5cm}
-\begin{center}
-\includegraphics[totalheight=.22\textheight,
-width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
-\end{center}
-\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
-\label{fig:example-model}
-\end{figure}
-\vspace{-0.3cm}
-\begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
-Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
-In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
-\end{remark}
-
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
-
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
-
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
-
-\smallskip
-\begin{theorem}\label{thm:existence-NE}
-The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
-\end{theorem}
-
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
-Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.
-
-\section{Characterization of NE v.s Randomization}\label{sec:main-I}
-
-In this section we first characterize the equilibrium points of the CSR game as maximizers of a proper function.
-Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values.
-The explicit form of this function and some of its properties has been given in the following lemma:
-
-\smallskip
-\begin{lemma}\label{lem:NE-characterization}
-Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$.
-Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game.
-\end{lemma} 
-\begin{proof}
-For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
-In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}).
-But this is in contradiction with $P^*$ being an equilibrium.
-Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$.
-Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
-On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
-Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.
-\end{proof}
-
-\smallskip
-Using Lemma \ref{lem:NE-characterization}, the problem of finding NE of the system reduces to finding the maximizers of the function $f(\cdot)$.
-In other words, if we have an efficient algorithm which can find the global maximum of $f(\cdot)$, then we will be able to find the equilibrium points of the system efficiently.
-Note that here $f(\cdot)$ is not a potential function of the game, however, it can be used to drive the search process to an equilibrium.
-In the following theorem we show that randomization can be quite useful for maximizing such function when the players' neighborhoods are not saturated with many resources.
-
-\smallskip
-\begin{theorem}\label{thm:randomization}
-Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
-\end{theorem}
-\begin{proof}  
-Let us consider an arbitrary player $i$ such that $M_i(t)\leq \sqrt{|O|}$, and let him uniformly and independently update to one of the possible $|O|$ resources, each with probability $\frac{1}{|O|}$.
-We compute the expected amount of $\mathbb{E}[f(t+1)]$.
-For this purpose we first consider the expected change in $\mathbb{E}[M_i(t+1)]$:
-\begin{align}\nonumber
-\mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
-&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
-\end{align}
-where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
-
-Next for any other node $j$ such that $i\in B(j, r_j(t)), j\neq i$ we can write
-\begin{align}\nonumber
-\mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
-&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
-\end{align}
-where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
-Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$).
-Therefore, we can write
-\begin{align}\nonumber
-&\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
-&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr 
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
-\end{align}
-where the last two inequalities is due to the fact that $M_i(t)\leq \sqrt{|O|}, \forall i$.
-Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$.
-In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
-\end{proof}
-
-In fact, Theorem \ref{thm:randomization} guarantees a good improvement in the value of the objective function $f$ as long as there are not too many resources around each player.
-However, when the system gets closer to its equilibrium points, the speed of progress can be much slower, or there may exist a possibility where the objective function gets stuck in one of its local maximums.
-To circumvent this issue, we introduce a random tree based search algorithm such that with non vanishing probability the algorithm can always escape from the local maximums, and hence steer the search toward global maximum of the objective function.
-
-\section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
-
-\section{Conclusion}\label{sec:conclusion}
-In this paper, we have studied the binary-preference capacitated selfish replication (CSR) game over general networks.
-We have characterized the equilibrium points of the system using a proper objective function.
-We leveraged this objective function and proposed a randomized algorithm based on the random tree search to find the global maximizers of this function, and hence, the NE points of the system.
-As an avenue for future research, one possibility is to study the dynamic version of the $CSR$ game, in the spirit of what has been discussed in \cite{fabrikant2003network}.
-
+\input{abstract.tex}
+\input{introduction.tex}
+\input{problem.tex}
+\input{motivation.tex}
+\input{algorithm.tex}
+\input{conclusion.tex}
 \bibliographystyle{IEEEtran}

### 2016-03-02 doc/problem.tex
breaking down the paper

\section{Problem Formulation and Existing Results}\label{sec:game-model}

In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}. In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.

\subsection{CSR Game Model}
We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$. We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$. For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache. All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below). Moreover, we assume that each node has access to all the resources. For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
\begin{align}\label{eq:CSR-cost-formulation}
C_i(P)=\sum_{o\in O\setminus \{P_i\}}d_{\mathcal{G}}(i, \sigma_i(P,o)),
\end{align}
where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$. Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$. Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network. We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity. In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.

\begin{figure}[htb]
\vspace{-1.5cm}
\begin{center}
\includegraphics[totalheight=.22\textheight,
width=.4\textwidth,viewport=-50 0 800 750]{example} \hspace{0.4in}
\end{center}
\vspace{-0.3cm}\caption{CSR game with $n=11$ players and $O=\{o_1,o_2,o_3\}$ resources. We have $C_1(P)=0+1+1=2, C_8(P)=0+1+2=3$ and $r_1(P)=1, r_8(P)=1$.}
\label{fig:example-model}
\end{figure}
\vspace{-0.3cm}
\begin{remark}
If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$. Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network. In the case where $n < |O|$, all the players will allocate different resources and the game becomes trivial, hence we can simply assume that $n \ge |O|$.
\end{remark}

\begin{remark}\label{rem:varying-cache}
Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
\end{remark}

\begin{remark}\label{rem:cost-to-radius}
Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$. This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
\end{remark}

It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely

\smallskip
\begin{theorem}\label{thm:existence-NE}
The CSR game admits an ordinal potential function, and hence, a pure-strategy Nash equilibrium.
\end{theorem}

Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$). Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.

### 2016-03-02 src/graph.cpp
implemented the random graph generator

@@ -1,0 +1,52 @@
+#include <random>
+#include <time.h>
+#include <array>
+#include <cmath>
+#include <string>
+#include <sstream>
+#include "graph.h"
+
+
+Graph::Graph(){
+}
+
+Graph::~Graph(){
+    for(int i=0;i<nodes.size();i++){
+        delete nodes[i];
+    }
+}
+
+//very simple random graph generator
+//incrementally constructs the graph, vertex by vertex
+//randomly connects the new vertex to at least p other vertices (no guarantees for the first p-vertices)
+//todo: replace this with Erdos random graphs
+void Graph::generateRandomGraph(int size, int p){
+    std::mt19937 rng;
+    std::array<int, 624> seed_data;
+    std::random_device r;
+    std::generate_n(seed_data.data(), seed_data.size(), std::ref(r));
+    std::seed_seq seq(std::begin(seed_data), std::end(seed_data));
+    rng.seed(seq);
+    std::uniform_int_distribution<uint32_t> uint_dist;
+    
+    for(int i=0;i<size;i++){
+        Node* v = new Node(i);
+        int j=0;
+        while(j<std::min(i,p)){
+            auto u = uint_dist(rng)%i;
+            if(v->addEdge(nodes[u])){
+                j++;
+            }
+        }
+        nodes.push_back(v);
+    }
+}
+
+std::string Graph::toString(){
+    std::stringstream ss;
+    for(int i=0;i<nodes.size();i++){
+        ss << i << ":" << nodes[i]->toString() << std::endl ;
+
+    }
+    return ss.str();
+}

### 2016-03-02 src/graph.h

@@ -1,0 +1,12 @@
+#pragma once
+#include <vector>
+#include "node.h"
+
+class Graph{
+public:
+    Graph();
+    ~Graph();
+    std::vector<Node*> nodes;
+    void generateRandomGraph(int size, int p);
+    std::string toString();
+};

### 2016-03-02 src/main.cpp

@@ -1,5 +1,11 @@
 #include <iostream>
+#include "graph.h"
+
+using namespace std;
 
 int main(int argc, const char * argv[]) {
-    return 0;
+    Graph* g = new Graph();
+    g->generateRandomGraph(100, 5);
+    cout << g->toString() << endl ;
+
 }

### 2016-03-02 src/node.cpp

@@ -1,0 +1,33 @@
+#include "node.h"
+#include <algorithm>
+#include <sstream>
+#include <string>
+
+Node::Node(int _id){
+    id=_id;
+}
+
+//creates an edge between this node and node v
+//returns true if successfull, returns false if the edge already exists.
+bool Node::addEdge(Node * v){
+    //first, check if this edge already exists
+    auto it = find(adjacencyList.begin(), adjacencyList.end(), v);
+    if(it != adjacencyList.end()){
+        //the edge between this and node v already exists. do not make duplicate edges
+        return false;
+    }else{
+        // add the edge between this and node v
+        v->adjacencyList.push_back(this);
+        adjacencyList.push_back(v);
+        return true;
+    }
+}
+
+std::string Node::toString(){
+    std::stringstream ss;
+    for(int i=0;i<adjacencyList.size();i++){
+        ss << adjacencyList[i]->id << ", " ;
+    }
+    ss << std::endl;
+    return ss.str();
+}

### 2016-03-02 src/node.h

@@ -1,0 +1,14 @@
+#pragma once
+
+#include <string>
+#include<vector>
+
+class Node{
+public:
+    Node(int);
+    int id;
+    int color;
+    std::vector<Node*> adjacencyList;
+    bool addEdge(Node*);
+    std::string toString();
+};

### 2016-03-03 src/graph.cpp
implemented profile and cost function

@@ -6,7 +6,6 @@
 #include <sstream>
 #include "graph.h"
 
-
 Graph::Graph(){
 }
 

### 2016-03-03 src/main.cpp

@@ -1,11 +1,19 @@
 #include <iostream>
 #include "graph.h"
+#include "profile.h"
 
 using namespace std;
 
 int main(int argc, const char * argv[]) {
     Graph* g = new Graph();
-    g->generateRandomGraph(100, 5);
-    cout << g->toString() << endl ;
-
+    int playerSize = 10;
+    int graphConnectivityFactor=2;
+    int resourceSize = 3;
+    g->generateRandomGraph(playerSize, graphConnectivityFactor);
+    Profile* p = new Profile(playerSize, resourceSize);
+    p->generateRandomProfile();
+    int c0 =p->cost(g->nodes[g->nodes.size()-1]);
+    cout << "cost="<< c0 << endl ;
+    //cout << g->toString() << endl ;
+    return 0;
 }

### 2016-03-03 src/node.h

@@ -1,13 +1,13 @@
 #pragma once
 
 #include <string>
-#include<vector>
+#include <vector>
 
 class Node{
 public:
+    bool visited;   //used for BFS
+    int id;    
     Node(int);
-    int id;
-    int color;
     std::vector<Node*> adjacencyList;
     bool addEdge(Node*);
     std::string toString();

### 2016-03-03 src/profile.cpp

@@ -1,0 +1,105 @@
+#include "profile.h"
+#include <algorithm>
+#include <iostream>
+#include <sstream>
+#include <string>
+#include <array>
+#include <limits>
+#include <set>
+#include <list>
+
+Profile::Profile(int s, int r){
+    size=s;
+    resources=r;
+    allocation = std::vector<int>(size);
+    
+    std::array<int, 624> seed_data;
+    std::random_device random_device;
+    std::generate_n(seed_data.data(), seed_data.size(), std::ref(random_device));
+    std::seed_seq seq(std::begin(seed_data), std::end(seed_data));
+    rng.seed(seq);
+}
+
+Profile::~Profile(){
+}
+
+void Profile::generateRandomProfile(){
+    std::uniform_int_distribution<uint32_t> uint_dist;
+    // ensures no missing resources in the profile
+    for(int i=0;i<resources;i++){
+        allocation[i] = i;
+    }
+    //fill up the rest of the profile randomly
+    for(int i=resources;i<size;i++){
+        allocation[i] = uint_dist(rng)%resources;
+    }
+    //shuffle the allocation a couple of times
+    for(int i=0;i<resources*size;i++){
+        std::swap(allocation[uint_dist(rng)%size], allocation[uint_dist(rng)%size]);
+        std::next_permutation(allocation.begin(), allocation.end());
+    }
+}
+
+std::string Profile::toString(){
+    std::stringstream ss;
+    for(int i=0;i<size;i++){
+        ss << allocation[i] << ", " ;
+    }
+    ss << std::endl;
+    return ss.str();
+}
+
+// computes the sum cost for the player v
+// To compute the sum cost, we execute breath-first search from node v
+// along the path, whenever we see a resource, we update it's cost (the distance from node v)
+// we continue until we have visited all resources or we finish the graph
+int Profile::cost(Node* v){
+    std::list<Node*> q; //bfs queue
+    std::vector<bool> visited(size);
+    std::vector<int> distance(size);
+    std::vector<int> mininimumResourceDistance(resources);
+    for(int i=0;i<size;i++){
+        visited[i]=false;
+        distance[i]=std::numeric_limits<int>::max();
+    }
+    for(int i=0;i<resources;i++){
+        mininimumResourceDistance[i]=std::numeric_limits<int>::max();
+    }
+    distance[v->id]=0;
+    visited[v->id]=true;
+    mininimumResourceDistance[allocation[v->id]]=0;
+    
+    q.push_back(v);
+
[…]

### 2016-03-03 src/profile.h

@@ -1,0 +1,18 @@
+#pragma once
+#include <random>
+#include <string>
+#include <vector>
+#include "node.h"
+
+class Profile{
+    int size;
+    int resources;
+    std::vector<int> allocation; //resource allocation for each nodes
+    std::mt19937 rng;
+public:
+    Profile(int size, int resources);
+    ~Profile();
+    std::string toString();
+    int cost(Node*);
+    void generateRandomProfile();
+};

### 2016-03-04 src/graph.cpp
implemented Erdos-Renyi random graph model

@@ -1,4 +1,5 @@
 #include <random>
+#include <iostream>
 #include <time.h>
 #include <array>
 #include <cmath>
@@ -38,6 +39,43 @@ void Graph::generateRandomGraph(int size, int p){
             }
         }
         nodes.push_back(v);
+    }
+}
+
+// Generates a random graph of size "size"
+// The p is the probabiliy that there exists an edge between two vertices i and j
+// Furthermore, we ensure that the graph is connected by connecting every node i to i+1 (without losing any generality)
+void Graph::generateErdosRenyiRandomGraph(int size, double p){
+    //step 0: setup random number generator
+    std::mt19937 rng;
+    std::array<int, 624> seed_data;
+    std::random_device r;
+    std::generate_n(seed_data.data(), seed_data.size(), std::ref(r));
+    std::seed_seq seq(std::begin(seed_data), std::end(seed_data));
+    rng.seed(seq);
+    std::uniform_real_distribution<> dis(0, 1);
+
+    //step 1: generate n nodes
+    for(int i=0;i<size;i++){
+        Node* v = new Node(i);
+        nodes.push_back(v);
+    }
+    
+    //step 1: make sure the graph is connected
+    for(int i=0;i<size-1;i++){
+        nodes[i]->addEdge(nodes[i+1]);
+    }
+    
+    //step 2: randomly generate edges
+    for(int i=0;i<size;i++){
+        for(int j=0;j<size;j++){
+            if(i!=j){
+                double prob = dis(rng);
+                if(prob<p){
+                    nodes[i]->addEdge(nodes[j]);
+                }
+            }
+        }
     }
 }
 

### 2016-03-04 src/graph.h

@@ -8,5 +8,6 @@ public:
     ~Graph();
     std::vector<Node*> nodes;
     void generateRandomGraph(int size, int p);
+    void generateErdosRenyiRandomGraph(int size, double p);
     std::string toString();
 };

### 2016-03-04 src/main.cpp

@@ -9,11 +9,12 @@ int main(int argc, const char * argv[]) {
     int playerSize = 10;
     int graphConnectivityFactor=2;
     int resourceSize = 3;
-    g->generateRandomGraph(playerSize, graphConnectivityFactor);
+    //g->generateRandomGraph(playerSize, graphConnectivityFactor);
+    g->generateErdosRenyiRandomGraph(playerSize, 0.1);
     Profile* p = new Profile(playerSize, resourceSize);
     p->generateRandomProfile();
     int c0 =p->cost(g->nodes[g->nodes.size()-1]);
     cout << "cost="<< c0 << endl ;
-    //cout << g->toString() << endl ;
+    cout << g->toString() << endl ;
     return 0;
 }

### 2016-03-04 src/graph.cpp
Initial compile on windows

@@ -5,8 +5,8 @@
 #include <cmath>
 #include <string>
 #include <sstream>
+#include <cstdint>
 #include "graph.h"
-
 Graph::Graph(){
 }
 

### 2016-03-04 src/main.cpp

@@ -5,16 +5,17 @@
 using namespace std;
 
 int main(int argc, const char * argv[]) {
-    Graph* g = new Graph();
-    int playerSize = 10;
-    int graphConnectivityFactor=2;
-    int resourceSize = 3;
-    //g->generateRandomGraph(playerSize, graphConnectivityFactor);
-    g->generateErdosRenyiRandomGraph(playerSize, 0.1);
-    Profile* p = new Profile(playerSize, resourceSize);
-    p->generateRandomProfile();
-    int c0 =p->cost(g->nodes[g->nodes.size()-1]);
-    cout << "cost="<< c0 << endl ;
-    cout << g->toString() << endl ;
+	Graph* g = new Graph();
+	int playerSize = 10;
+	int graphConnectivityFactor = 2;
+	int resourceSize = 3;
+	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
+	g->generateErdosRenyiRandomGraph(playerSize, 0.1);
+	Profile* p = new Profile(playerSize, resourceSize);
+	p->generateRandomProfile();
+	int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
+	cout << "cost=" << c0 << endl;
+	cout << g->toString() << endl;
+	system("PAUSE");
     return 0;
 }

### 2016-03-04 src/profile.cpp

@@ -7,6 +7,8 @@
 #include <limits>
 #include <set>
 #include <list>
+#include <cstdint>
+#include <numeric>
 
 Profile::Profile(int s, int r){
     size=s;

### 2016-03-04 src/graph.cpp
implemented the update radius function

@@ -7,6 +7,7 @@
 #include <sstream>
 #include <cstdint>
 #include "graph.h"
+
 Graph::Graph(){
 }
 

### 2016-03-04 src/main.cpp

@@ -6,16 +6,20 @@ using namespace std;
 
 int main(int argc, const char * argv[]) {
 	Graph* g = new Graph();
-	int playerSize = 10;
+	int playerSize = 20;
 	int graphConnectivityFactor = 2;
-	int resourceSize = 3;
+	int resourceSize = 5;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
-	g->generateErdosRenyiRandomGraph(playerSize, 0.1);
+	g->generateErdosRenyiRandomGraph(playerSize, 0.05);
 	Profile* p = new Profile(playerSize, resourceSize);
 	p->generateRandomProfile();
 	int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
 	cout << "cost=" << c0 << endl;
 	cout << g->toString() << endl;
+	cout << "-------------------" << endl;
+	for (int i = 0; i < playerSize; i++){
+		cout << "***" << p->updateRadius(g->nodes[i]) << endl;	
+	}
 	system("PAUSE");
     return 0;
 }

### 2016-03-04 src/profile.cpp

@@ -14,7 +14,7 @@ Profile::Profile(int s, int r){
     size=s;
     resources=r;
     allocation = std::vector<int>(size);
-    
+	radius = std::vector<int>(size);
     std::array<int, 624> seed_data;
     std::random_device random_device;
     std::generate_n(seed_data.data(), seed_data.size(), std::ref(random_device));
@@ -49,6 +49,42 @@ std::string Profile::toString(){
     }
     ss << std::endl;
     return ss.str();
+}
+
+//Find the closest node to node v that has the same allocation as v
+int Profile::updateRadius(Node* v){
+	int result = size;	//ideally should be diameter of the graph+1, but size would be fine
+	std::list<Node*> q; //bfs queue
+	std::vector<int> distance(size);
+	std::vector<bool> visited(size);
+	for (int i = 0; i < size; i++){
+		visited[i] = false;
+		distance[i] = std::numeric_limits<int>::max();
+	}
+	distance[v->id] = 0;
+	visited[v->id] = true;
+	q.push_back(v);
+
+	while (!q.empty()){
+		auto u = q.front(); q.pop_front();
+		for (int i = 0; i<u->adjacencyList.size(); i++){
+			auto w = u->adjacencyList[i];
+			if (!visited[w->id]){
+				if (distance[w->id] > distance[u->id] + 1){
+					distance[w->id] = distance[u->id] + 1;
+				}
+				if (allocation[w->id] == allocation[v->id]){
+					if (distance[w->id] < result){
+						std::cout << w->id << " " << v->id << " " << allocation[w->id] << " " <<allocation[v->id] << " " << distance[w->id] << " " << result << std::endl;
+						result = distance[w->id];
+					}
+				}
+				visited[w->id] = true;
+				q.push_back(w);
+			}
+		}
+	}
+	return result;
 }
 
 // computes the sum cost for the player v

### 2016-03-04 src/profile.h

@@ -7,7 +7,11 @@
 class Profile{
     int size;
     int resources;
-    std::vector<int> allocation; //resource allocation for each nodes
+	//resource allocation for each nodes, each allocation[i] can take a value between 0..resources-1,
+	//indicating player i (\in [0..size-1])is holding resource j (\in [0..resources-1])
+    std::vector<int> allocation; 
+	//radius for each player: distance between node i and the nearest node other that i holding the same resource
+	std::vector<int> radius;
     std::mt19937 rng;
 public:
     Profile(int size, int resources);
@@ -15,4 +19,5 @@ public:
     std::string toString();
     int cost(Node*);
     void generateRandomProfile();
+	int updateRadius(Node* v);
 };

### 2016-03-05 src/main.cpp
implemented the graph ball and objective function

@@ -14,12 +14,32 @@ int main(int argc, const char * argv[]) {
 	Profile* p = new Profile(playerSize, resourceSize);
 	p->generateRandomProfile();
 	int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
+	p->updateRadius(g);
 	cout << "cost=" << c0 << endl;
 	cout << g->toString() << endl;
 	cout << "-------------------" << endl;
 	for (int i = 0; i < playerSize; i++){
 		cout << "***" << p->updateRadius(g->nodes[i]) << endl;	
 	}
+	cout << "*******************" << endl;
+	for (int i = 0; i < playerSize; i++){
+		cout << p->radius[i] << endl;
+	}
+	cout << "*******************" << endl;
+	for (int i = 0; i < playerSize; i++){
+		cout << p->objective(g->nodes[i]) << endl;
+	}
+	cout << "*******************" << endl;
+	cout << p->objectiveSum(g) << endl;
+	int max = -1;
+	for (int i = 0; i < 100; i++){
+		p->generateRandomProfile();
+		p->updateRadius(g);
+		int o = p->objectiveSum(g);
+		if (o>max) max = o ;
+		cout << o << endl;
+	}
+	cout << "Maximum Objective= " << max << endl;
 	system("PAUSE");
     return 0;
 }

### 2016-03-05 src/profile.cpp

@@ -51,6 +51,13 @@ std::string Profile::toString(){
     return ss.str();
 }
 
+int Profile::updateRadius(Graph* g){
+	for (int i = 0; i < size; i++){
+		radius[i] = updateRadius(g->nodes[i]);
+	}
+	return 0;
+}
+
 //Find the closest node to node v that has the same allocation as v
 int Profile::updateRadius(Node* v){
 	int result = size;	//ideally should be diameter of the graph+1, but size would be fine
@@ -75,7 +82,7 @@ int Profile::updateRadius(Node* v){
 				}
 				if (allocation[w->id] == allocation[v->id]){
 					if (distance[w->id] < result){
-						std::cout << w->id << " " << v->id << " " << allocation[w->id] << " " <<allocation[v->id] << " " << distance[w->id] << " " << result << std::endl;
+						//std::cout << w->id << " " << v->id << " " << allocation[w->id] << " " <<allocation[v->id] << " " << distance[w->id] << " " << result << std::endl;
 						result = distance[w->id];
 					}
 				}
@@ -85,6 +92,54 @@ int Profile::updateRadius(Node* v){
 		}
 	}
 	return result;
+}
+
+int Profile::objectiveSum(Graph* g){
+	int result = 0;
+	for (int i = 0; i < size; i++){
+		result += objective(g->nodes[i]);
+	}
+	return result;
+}
+
+//the objective function computes the number of different resources in the ball of size r_i around node v
+int Profile::objective(Node* v){
+	int r = radius[v->id];
+	std::list<Node*> q; //bfs queue
+	std::vector<int> distance(size);
+	std::vector<bool> visited(size);
+	for (int i = 0; i < size; i++){
+		visited[i] = false;
+		distance[i] = std::numeric_limits<int>::max();
+	}
+	distance[v->id] = 0;
+	visited[v->id] = true;
+	q.push_back(v);
+	bool ball_covered = false; 
+	while(!ball_covered & !q.empty()){
+		auto u = q.front(); q.pop_front();
+		for (int i = 0; i<u->adjacencyList.size(); i++){
+			auto w = u->adjacencyList[i];
+			if (!visited[w->id]){			
+				if (distance[w->id] > distance[u->id] + 1){
+					distance[w->id] = distance[u->id] + 1;
+				}			
+				if (distance[w->id] > r){
+					ball_covered = true;
+				}
+				visited[w->id] = true;
[…]

### 2016-03-05 src/profile.h

@@ -3,8 +3,10 @@
 #include <string>
 #include <vector>
 #include "node.h"
+#include "graph.h"
 
 class Profile{
+public:
     int size;
     int resources;
 	//resource allocation for each nodes, each allocation[i] can take a value between 0..resources-1,
@@ -13,11 +15,14 @@ class Profile{
 	//radius for each player: distance between node i and the nearest node other that i holding the same resource
 	std::vector<int> radius;
     std::mt19937 rng;
-public:
+
     Profile(int size, int resources);
     ~Profile();
     std::string toString();
     int cost(Node*);
     void generateRandomProfile();
+	int updateRadius(Graph* g);
 	int updateRadius(Node* v);
+	int objective(Node* v);
+	int objectiveSum(Graph* g);
 };

### 2016-03-08 src/main.cpp
added terminating condition using saturated neighborhoods

@@ -15,6 +15,9 @@ int main(int argc, const char * argv[]) {
 	p->generateRandomProfile();
 	int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
 	p->updateRadius(g);
+    p->updateSaturation(g);
+    cout << " ##############" << endl ;
+
 	cout << "cost=" << c0 << endl;
 	cout << g->toString() << endl;
 	cout << "-------------------" << endl;
@@ -38,6 +41,7 @@ int main(int argc, const char * argv[]) {
 		int o = p->objectiveSum(g);
 		if (o>max) max = o ;
 		cout << o << endl;
+        p->updateSaturation(g);
 	}
 	cout << "Maximum Objective= " << max << endl;
 	system("PAUSE");

### 2016-03-08 src/profile.cpp

@@ -15,6 +15,7 @@ Profile::Profile(int s, int r){
     resources=r;
     allocation = std::vector<int>(size);
 	radius = std::vector<int>(size);
+    saturation = std::vector<int>(size);
     std::array<int, 624> seed_data;
     std::random_device random_device;
     std::generate_n(seed_data.data(), seed_data.size(), std::ref(random_device));
@@ -51,11 +52,59 @@ std::string Profile::toString(){
     return ss.str();
 }
 
+int Profile::updateSaturation(Graph* g){
+    auto unsaturatedNeighbors=0;
+    for (auto i = 0; i < size; i++){
+        saturation[i] = updateSaturation(g->nodes[i]);
+        if(saturation[i]<=sqrt(resources))
+            unsaturatedNeighbors++;
+    }
+    std::cout << " UNSATURATED NEIGHBORS = " << unsaturatedNeighbors << std::endl ;
+    return unsaturatedNeighbors;
+}
+
+int Profile::updateSaturation(Node* v){
+    auto r = radius[v->id];
+    std::list<Node*> q; //bfs queue
+    std::vector<int> distance(size);
+    std::vector<bool> visited(size);
+    std::vector<int> visitedResources(resources);
+    
+    for (int i = 0; i < size; i++){
+        visited[i] = false;
+        distance[i] = std::numeric_limits<int>::max();
+    }
+    for(int i=0;i<resources;i++){
+        visitedResources[i]=0;
+    }
+    distance[v->id] = 0;
+    visited[v->id] = true;
+    q.push_back(v);
+
+    while (!q.empty()){
+        auto u = q.front(); q.pop_front();
+        for (int i = 0; i<u->adjacencyList.size(); i++){
+            auto w = u->adjacencyList[i];
+            if (!visited[w->id]){
+                if (distance[w->id] > distance[u->id] + 1){
+                    distance[w->id] = distance[u->id] + 1;
+                }
+                visited[w->id] = true;
+                if(distance[w->id] < r){
+                    q.push_back(w);
+                    visitedResources[allocation[w->id]]=1;
+                }
+            }
+        }
+    }
+    return std::accumulate(visitedResources.begin(), visitedResources.end(), 0);
+}
+
 int Profile::updateRadius(Graph* g){
-	for (int i = 0; i < size; i++){
-		radius[i] = updateRadius(g->nodes[i]);
-	}
-	return 0;
+    for (int i = 0; i < size; i++){
[…]

### 2016-03-08 src/profile.h

@@ -14,6 +14,9 @@ public:
     std::vector<int> allocation; 
 	//radius for each player: distance between node i and the nearest node other that i holding the same resource
 	std::vector<int> radius;
+    //determines the number of resources around the neighborhood of size radius(i) of each node i
+    std::vector<int> saturation;
+    
     std::mt19937 rng;
 
     Profile(int size, int resources);
@@ -25,4 +28,7 @@ public:
 	int updateRadius(Node* v);
 	int objective(Node* v);
 	int objectiveSum(Graph* g);
+    
+    int updateSaturation(Graph* g);
+    int updateSaturation(Node* v);
 };

### 2016-03-08 src/profile.cpp
added copy constructor for profile class

@@ -23,6 +23,19 @@ Profile::Profile(int s, int r){
     rng.seed(seq);
 }
 
+Profile::Profile(Profile* copy){
+    size=copy->size;
+    resources=copy->resources;
+    allocation = std::vector<int>(copy->allocation);
+    radius = std::vector<int>(copy->radius);
+    saturation = std::vector<int>(copy->saturation);
+    std::array<int, 624> seed_data;
+    std::random_device random_device;
+    std::generate_n(seed_data.data(), seed_data.size(), std::ref(random_device));
+    std::seed_seq seq(std::begin(seed_data), std::end(seed_data));
+    rng.seed(seq);
+}
+
 Profile::~Profile(){
 }
 

### 2016-03-08 src/profile.h

@@ -20,6 +20,7 @@ public:
     std::mt19937 rng;
 
     Profile(int size, int resources);
+    Profile(Profile* copy);
     ~Profile();
     std::string toString();
     int cost(Node*);

### 2016-03-08 src/main.cpp
implemented local steps in profile

@@ -36,12 +36,15 @@ int main(int argc, const char * argv[]) {
 	cout << p->objectiveSum(g) << endl;
 	int max = -1;
 	for (int i = 0; i < 100; i++){
-		p->generateRandomProfile();
-		p->updateRadius(g);
+        p->flip(g, g->nodes[i%playerSize]);
+        p->updateRadius(g);
+        cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
+		//p->generateRandomProfile();
+		//p->updateRadius(g);
 		int o = p->objectiveSum(g);
 		if (o>max) max = o ;
 		cout << o << endl;
-        p->updateSaturation(g);
+        //p->updateSaturation(g);
 	}
 	cout << "Maximum Objective= " << max << endl;
 	system("PAUSE");

### 2016-03-08 src/profile.cpp

@@ -72,7 +72,6 @@ int Profile::updateSaturation(Graph* g){
         if(saturation[i]<=sqrt(resources))
             unsaturatedNeighbors++;
     }
-    std::cout << " UNSATURATED NEIGHBORS = " << unsaturatedNeighbors << std::endl ;
     return unsaturatedNeighbors;
 }
 
@@ -257,4 +256,12 @@ int Profile::cost(Node* v){
     //}
     int result = std::accumulate(mininimumResourceDistance.begin(), mininimumResourceDistance.end(), 0);
     return result;
+}
+
+// randomly changes the resource stored on node v
+void Profile::flip(Graph* g, Node* v){
+    std::uniform_int_distribution<uint32_t> uint_dist;
+    allocation[v->id] = uint_dist(rng)%resources;
+    updateRadius(g);
+    updateSaturation(g);
 }

### 2016-03-08 src/profile.h

@@ -32,4 +32,6 @@ public:
     
     int updateSaturation(Graph* g);
     int updateSaturation(Node* v);
+    
+    void flip(Graph* g, Node* v);
 };

### 2016-03-09 src/main.cpp
added the search class
search class holds the top K closest nodes in a buffer

@@ -1,6 +1,7 @@
 #include <iostream>
 #include "graph.h"
 #include "profile.h"
+#include "search.h"
 
 using namespace std;
 
@@ -11,42 +12,12 @@ int main(int argc, const char * argv[]) {
 	int resourceSize = 5;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
 	g->generateErdosRenyiRandomGraph(playerSize, 0.05);
-	Profile* p = new Profile(playerSize, resourceSize);
-	p->generateRandomProfile();
-	int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
-	p->updateRadius(g);
-    p->updateSaturation(g);
-    cout << " ##############" << endl ;
-
-	cout << "cost=" << c0 << endl;
-	cout << g->toString() << endl;
-	cout << "-------------------" << endl;
-	for (int i = 0; i < playerSize; i++){
-		cout << "***" << p->updateRadius(g->nodes[i]) << endl;	
-	}
-	cout << "*******************" << endl;
-	for (int i = 0; i < playerSize; i++){
-		cout << p->radius[i] << endl;
-	}
-	cout << "*******************" << endl;
-	for (int i = 0; i < playerSize; i++){
-		cout << p->objective(g->nodes[i]) << endl;
-	}
-	cout << "*******************" << endl;
-	cout << p->objectiveSum(g) << endl;
-	int max = -1;
-	for (int i = 0; i < 100; i++){
-        p->flip(g, g->nodes[i%playerSize]);
-        p->updateRadius(g);
-        cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
-		//p->generateRandomProfile();
-		//p->updateRadius(g);
-		int o = p->objectiveSum(g);
-		if (o>max) max = o ;
-		cout << o << endl;
-        //p->updateSaturation(g);
-	}
-	cout << "Maximum Objective= " << max << endl;
-	system("PAUSE");
+    Search* search = new Search(playerSize, resourceSize, g);
+    //search->run();
+    search->run();
+    delete search;
+    delete g;
+    
+    system("PAUSE");
     return 0;
 }

### 2016-03-09 src/search.cpp

@@ -1,0 +1,99 @@
+#include <random>
+#include <iostream>
+#include <time.h>
+#include <array>
+#include <cmath>
+#include <string>
+#include <sstream>
+
+
+#include "search.h"
+
+
+template <class T, class S, class C>
+S& Container(priority_queue<T, S, C>& q) {
+    struct Queue : private priority_queue<T, S, C> {
+        static S& Container(priority_queue<T, S, C>& q) {
+            return q.*&Queue::c;
+        }
+    };
+    return Queue::Container(q);
+}
+
+Search::Search(int ps, int rs, Graph* gg){
+    playerSize = ps;
+    resourceSize = rs;
+    g=gg;
+    buffersize=50;
+    buffer = Container(pq);
+}
+
+Search::~Search(){
+}
+
+void Search::run(){
+    Profile* p = new Profile(playerSize, resourceSize);
+    p->generateRandomProfile();
+    int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
+    p->updateRadius(g);
+    p->updateSaturation(g);
+    cout << " ##############" << endl ;
+    
+    cout << "cost=" << c0 << endl;
+    cout << g->toString() << endl;
+    cout << "-------------------" << endl;
+    for (int i = 0; i < playerSize; i++){
+        cout << "***" << p->updateRadius(g->nodes[i]) << endl;
+    }
+    cout << "*******************" << endl;
+    for (int i = 0; i < playerSize; i++){
+        cout << p->radius[i] << endl;
+    }
+    cout << "*******************" << endl;
+    for (int i = 0; i < playerSize; i++){
+        cout << p->objective(g->nodes[i]) << endl;
+    }
+    cout << "*******************" << endl;
+    cout << p->objectiveSum(g) << endl;
+    int max = -1;
+    for (int i = 0; i < 100; i++){
+        p->flip(g, g->nodes[i%playerSize]);
+        p->updateRadius(g);
+        cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
+        //p->generateRandomProfile();
+        //p->updateRadius(g);
+        int o = p->objectiveSum(g);
+        if (o>max) max = o ;
+        cout << o << endl;
+        //p->updateSaturation(g);
+    }
+    cout << "Maximum Objective= " << max << endl;
+    
+    for(int i=0;i<10000;i++){
+        push(rand()%1000);
+    }
+    
[…]

### 2016-03-09 src/search.h

@@ -1,0 +1,27 @@
+#pragma once
+#include <vector>
+#include <algorithm>
+#include <functional>
+#include <cstdint>
+#include <queue>
+#include "graph.h"
+#include "profile.h"
+
+using namespace std;
+
+class Search{
+    int playerSize;
+    int resourceSize;
+    Graph* g;
+    
+    int buffersize;
+    priority_queue<int, vector<int>, less<int> > pq;
+    vector<int> buffer;
+public:
+    Search(int, int, Graph*);
+    ~Search();
+    void run();
+    void push(int);
+    int sample();
+    int get(int);
+};

### 2016-03-10 src/main.cpp
basic search is working

@@ -7,7 +7,7 @@ using namespace std;
 
 int main(int argc, const char * argv[]) {
 	Graph* g = new Graph();
-	int playerSize = 20;
+	int playerSize = 100;
 	int graphConnectivityFactor = 2;
 	int resourceSize = 5;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);

### 2016-03-10 src/profile.cpp

@@ -11,6 +11,7 @@
 #include <numeric>
 
 Profile::Profile(int s, int r){
+    cost=-1;
     size=s;
     resources=r;
     allocation = std::vector<int>(size);
@@ -24,20 +25,36 @@ Profile::Profile(int s, int r){
 }
 
 Profile::Profile(Profile* copy){
+    cost = copy->cost;
     size=copy->size;
     resources=copy->resources;
-    allocation = std::vector<int>(copy->allocation);
-    radius = std::vector<int>(copy->radius);
-    saturation = std::vector<int>(copy->saturation);
+    allocation = std::vector<int>(size);
+    radius = std::vector<int>(size);
+    saturation = std::vector<int>(size);
+    //allocation = std::vector<int>(copy->allocation);
+    //radius = std::vector<int>(copy->radius);
+    //saturation = std::vector<int>(copy->saturation);
     std::array<int, 624> seed_data;
     std::random_device random_device;
     std::generate_n(seed_data.data(), seed_data.size(), std::ref(random_device));
     std::seed_seq seq(std::begin(seed_data), std::end(seed_data));
     rng.seed(seq);
+    for(int i=0;i<size;i++){
+        allocation[i] = copy->allocation[i];
+        radius[i] = copy->radius[i];
+        saturation[i] = copy->saturation[i];
+    }
 }
 
 Profile::~Profile(){
 }
+
+bool Profile::operator<(const Profile& right) const{
+    std::cout << cost << " " << right.cost << std::endl ;
+
+    return cost < right.cost;
+}
+
 
 void Profile::generateRandomProfile(){
     std::uniform_int_distribution<uint32_t> uint_dist;
@@ -160,6 +177,7 @@ int Profile::objectiveSum(Graph* g){
 	for (int i = 0; i < size; i++){
 		result += objective(g->nodes[i]);
 	}
+    cost=result;
 	return result;
 }
 
@@ -207,7 +225,7 @@ int Profile::objective(Node* v){
 // To compute the sum cost, we execute breath-first search from node v
 // along the path, whenever we see a resource, we update it's cost (the distance from node v)
 // we continue until we have visited all resources or we finish the graph
-int Profile::cost(Node* v){
+int Profile::computeCost(Node* v){
     std::list<Node*> q; //bfs queue
     std::vector<bool> visited(size);
     std::vector<int> distance(size);

### 2016-03-10 src/profile.h

@@ -1,5 +1,6 @@
 #pragma once
 #include <random>
+#include <iostream>
 #include <string>
 #include <vector>
 #include "node.h"
@@ -16,14 +17,17 @@ public:
 	std::vector<int> radius;
     //determines the number of resources around the neighborhood of size radius(i) of each node i
     std::vector<int> saturation;
+    int cost;
     
     std::mt19937 rng;
 
     Profile(int size, int resources);
     Profile(Profile* copy);
     ~Profile();
+    bool operator<(const Profile&) const; 
+    
     std::string toString();
-    int cost(Node*);
+    int computeCost(Node*);
     void generateRandomProfile();
 	int updateRadius(Graph* g);
 	int updateRadius(Node* v);
@@ -34,4 +38,17 @@ public:
     int updateSaturation(Node* v);
     
     void flip(Graph* g, Node* v);
+};
+
+
+class profileGreaterComparator{
+    public: bool operator()(const Profile* lhs, const Profile* rhs) const{
+        return lhs->cost > rhs->cost;
+    }
+};
+
+class profileLesserComparator{
+public: bool operator()(const Profile* lhs, const Profile* rhs) const{
+    return lhs->cost < rhs->cost;
+}
 };

### 2016-03-10 src/search.cpp

@@ -5,10 +5,7 @@
 #include <cmath>
 #include <string>
 #include <sstream>
-
-
 #include "search.h"
-
 
 template <class T, class S, class C>
 S& Container(priority_queue<T, S, C>& q) {
@@ -24,7 +21,7 @@ Search::Search(int ps, int rs, Graph* gg){
     playerSize = ps;
     resourceSize = rs;
     g=gg;
-    buffersize=50;
+    buffersize=10;
     buffer = Container(pq);
 }
 
@@ -32,57 +29,59 @@ Search::~Search(){
 }
 
 void Search::run(){
-    Profile* p = new Profile(playerSize, resourceSize);
-    p->generateRandomProfile();
-    int c0 = p->cost(g->nodes[g->nodes.size() - 1]);
-    p->updateRadius(g);
-    p->updateSaturation(g);
-    cout << " ##############" << endl ;
-    
-    cout << "cost=" << c0 << endl;
-    cout << g->toString() << endl;
-    cout << "-------------------" << endl;
-    for (int i = 0; i < playerSize; i++){
-        cout << "***" << p->updateRadius(g->nodes[i]) << endl;
-    }
-    cout << "*******************" << endl;
-    for (int i = 0; i < playerSize; i++){
-        cout << p->radius[i] << endl;
-    }
-    cout << "*******************" << endl;
-    for (int i = 0; i < playerSize; i++){
-        cout << p->objective(g->nodes[i]) << endl;
-    }
-    cout << "*******************" << endl;
-    cout << p->objectiveSum(g) << endl;
     int max = -1;
-    for (int i = 0; i < 100; i++){
-        p->flip(g, g->nodes[i%playerSize]);
+    int total_iteration = 10000;
+    int warmupPhase=total_iteration/20;
+    for (int i = 0; i < total_iteration; i++){
+        Profile* p;
+        if(i<warmupPhase){
+            p = new Profile(playerSize, resourceSize);
+            p->generateRandomProfile();
+        }else{
+            Profile* q = sample();
+            p = new Profile(q);
+            for(int j=0;j<1+0.1*total_iteration/i; j++){
+                //p->generateRandomProfile();
+                p->flip(g, g->nodes[rand()%playerSize]);
+            }
+
+        }
+
+        //int c0 = p->computeCost(g->nodes[g->nodes.size() - 1]);
         p->updateRadius(g);
-        cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
[…]

### 2016-03-10 src/search.h

@@ -15,13 +15,18 @@ class Search{
     Graph* g;
     
     int buffersize;
-    priority_queue<int, vector<int>, less<int> > pq;
-    vector<int> buffer;
+    //priority_queue<int, vector<int>, less<int> > pq;
+    //vector<int> buffer;
+    priority_queue<Profile*, vector<Profile*>, profileGreaterComparator > pq;
+    vector<Profile*> buffer;
+    
+    vector<Profile*> db;
 public:
+    
     Search(int, int, Graph*);
     ~Search();
     void run();
-    void push(int);
-    int sample();
-    int get(int);
+    void push(Profile*);
+    Profile* sample();
+    Profile* get(int);
 };

### 2016-03-10 doc/paper.tex
bugfix

@@
 Replication Games}
-\author{\authorblockN{Seyed Nematollah Ahmadian\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
+\author{\authorblockN{Seyed Nematollah Ahmadyan\textdagger, Seyed Rasoul Etesami\textdaggerdbl, H. Vincent Poor\textdaggerdbl}
   \authorblockA{}
-\thanks{\textdagger Seyed Nematollah Ahmadian is with
+\thanks{\textdagger Seyed Nematollah Ahmadyan is with
 Coordinated Science Laboratory,

### 2016-03-10 src/main.cpp

@@ -9,9 +9,9 @@ int main(int argc, const char * argv[]) {
 	Graph* g = new Graph();
 	int playerSize = 100;
 	int graphConnectivityFactor = 2;
-	int resourceSize = 5;
+	int resourceSize = 20;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
-	g->generateErdosRenyiRandomGraph(playerSize, 0.05);
+	g->generateErdosRenyiRandomGraph(playerSize, 0.025);
     Search* search = new Search(playerSize, resourceSize, g);
     //search->run();
     search->run();

### 2016-03-10 src/profile.cpp

@@ -160,7 +160,6 @@ int Profile::updateRadius(Node* v){
 				}
 				if (allocation[w->id] == allocation[v->id]){
 					if (distance[w->id] < result){
-						//std::cout << w->id << " " << v->id << " " << allocation[w->id] << " " <<allocation[v->id] << " " << distance[w->id] << " " << result << std::endl;
 						result = distance[w->id];
 					}
 				}
@@ -187,10 +186,16 @@ int Profile::objective(Node* v){
 	std::list<Node*> q; //bfs queue
 	std::vector<int> distance(size);
 	std::vector<bool> visited(size);
+    std::vector<int> visitedResources(resources);
+    
 	for (int i = 0; i < size; i++){
 		visited[i] = false;
 		distance[i] = std::numeric_limits<int>::max();
 	}
+    
+    for(int i=0;i<resources;i++){
+        visitedResources[i]=0;
+    }
 	distance[v->id] = 0;
 	visited[v->id] = true;
 	q.push_back(v);
@@ -205,20 +210,20 @@ int Profile::objective(Node* v){
 				}			
 				if (distance[w->id] > r){
 					ball_covered = true;
-				}
-				visited[w->id] = true;
-				q.push_back(w);
+                }else{
+                    visited[w->id] = true;
+                    q.push_back(w);
+                }
 			}
 		}
 	}
 
-	int ball = 0;
 	for (int i = 0; i < size; i++){
 		if (visited[i]){
-			ball++;
+            visitedResources[allocation[i]] = 1;
 		}
 	}
-	return ball;
+    return std::accumulate(visitedResources.begin(), visitedResources.end(), 0);
 }
 
 // computes the sum cost for the player v

### 2016-03-10 src/search.cpp

@@ -44,7 +44,6 @@ void Search::run(){
                 //p->generateRandomProfile();
                 p->flip(g, g->nodes[rand()%playerSize]);
             }
-
         }
 
         //int c0 = p->computeCost(g->nodes[g->nodes.size() - 1]);
@@ -54,6 +53,7 @@ void Search::run(){
 
 
         int o = p->objectiveSum(g);
+
         if (o>max) max = o ;
         db.push_back(p);
         push(p);
@@ -61,7 +61,7 @@ void Search::run(){
         //p->flip(g, g->nodes[i%playerSize]);
         //p->updateRadius(g);
         //cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
-        if(s==0){
+        if(o==playerSize*resourceSize){
             cout << " Found equilibrium point after " << i << " iterations" << endl ;
             cout << " Maximum Objective= " << max << endl;
             cout << " Buffer ----------- " << endl ;

### 2016-03-10 src/main.cpp
bugfix for saturation

@@ -9,9 +9,9 @@ int main(int argc, const char * argv[]) {
 	Graph* g = new Graph();
 	int playerSize = 100;
 	int graphConnectivityFactor = 2;
-	int resourceSize = 20;
+	int resourceSize = 5;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
-	g->generateErdosRenyiRandomGraph(playerSize, 0.025);
+	g->generateErdosRenyiRandomGraph(playerSize, 0.05);
     Search* search = new Search(playerSize, resourceSize, g);
     //search->run();
     search->run();

### 2016-03-10 src/profile.cpp

@@ -86,8 +86,14 @@ int Profile::updateSaturation(Graph* g){
     auto unsaturatedNeighbors=0;
     for (auto i = 0; i < size; i++){
         saturation[i] = updateSaturation(g->nodes[i]);
-        if(saturation[i]<=sqrt(resources))
+        if(saturation[i]!=resources){
             unsaturatedNeighbors++;
+         //   std::cout << "* " << saturation[i] << " " << resources << std::endl ;
+
+        }
+        
+        //if(saturation[i]<=sqrt(resources))
+        //    unsaturatedNeighbors++;
     }
     return unsaturatedNeighbors;
 }
@@ -109,8 +115,9 @@ int Profile::updateSaturation(Node* v){
     distance[v->id] = 0;
     visited[v->id] = true;
     q.push_back(v);
-
-    while (!q.empty()){
+    
+    bool ball_covered = false;
+    while(!ball_covered & !q.empty()){
         auto u = q.front(); q.pop_front();
         for (int i = 0; i<u->adjacencyList.size(); i++){
             auto w = u->adjacencyList[i];
@@ -118,10 +125,12 @@ int Profile::updateSaturation(Node* v){
                 if (distance[w->id] > distance[u->id] + 1){
                     distance[w->id] = distance[u->id] + 1;
                 }
-                visited[w->id] = true;
-                if(distance[w->id] < r){
-                    q.push_back(w);
+                if (distance[w->id] > r){
+                    ball_covered = true;
+                }else{
                     visitedResources[allocation[w->id]]=1;
+                    visited[w->id] = true;
+                    q.push_back(w);
                 }
             }
         }

### 2016-03-10 src/search.cpp

@@ -33,6 +33,7 @@ void Search::run(){
     int total_iteration = 10000;
     int warmupPhase=total_iteration/20;
     for (int i = 0; i < total_iteration; i++){
+        buffersize = 20 + log(i);
         Profile* p;
         if(i<warmupPhase){
             p = new Profile(playerSize, resourceSize);

### 2016-03-10 doc/introduction.tex
added paragraph about random tree

@@
 The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
+Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where "binary preferences" captures the behavioral pattern where players are equally interested in some objects.
 
-In this paper, we consider the capacitated selfish replication game with binary preferences.
+In this paper, we consider the \emph{Capacitated Selfish Replication (CSR)} game with binary preferences.
 In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
@@
 
+%##################
+
+We use random tree search algorithm to locate Nash equilibrium points in CSR game.
+The random tree search algorithm is an efficient randomized algorithm for searching the state space of games.
+The random tree algorithm works by sampling the allocation space of the CSR game.
+The algorithm searches for the optimum allocation, resulting in the Nash equilibrium.
+The random tree search is guided by maximizing a cost function associated with each allocation.
+The random tree grows multiple tree walks from an initial allocation.
+The random tree branches the simulation walks to bias the walk toward the optimim allocation and avoiding the local minimas.
+Recently, stochastic random tree-based search methods have emerged as an alternative to classic optimization algorithms.
+The random tree algorithm has been used to optimize analog circuits \cite{adel2015}, robotic motion planning \cite{Lavalle2006}, and deep learning\cite{silver2016}.
+In comparison to the classic optimization algorithms such as simulated annealing or hill climbing, the random tree search is more efficient and does not get stuck in local minimas \cite{adel15, Lavalle2006}.
+
+%##################
+
 The paper is organized as follows.
@@
 In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
+Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm to maximize the objective function.
+We demonstrate, through numerous simulations, this method is very effective for finding the equilibrium points on large scale graphs in practical settings.
 We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.

### 2016-03-10 src/main.cpp

@@ -9,7 +9,7 @@ int main(int argc, const char * argv[]) {
 	Graph* g = new Graph();
 	int playerSize = 100;
 	int graphConnectivityFactor = 2;
-	int resourceSize = 5;
+	int resourceSize = 10;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
 	g->generateErdosRenyiRandomGraph(playerSize, 0.05);
     Search* search = new Search(playerSize, resourceSize, g);

### 2016-03-10 doc/introduction.tex
Modifying Introduction

--- 2016-03-02 doc/introduction.tex
@@
 \section{Introduction}
-In recent years, there has been a wide range of studies on the role of social and distributed networks in various disciplinary areas such as economics, computer science, epidemiology, and engineering.
-In particular, availability of large data from online social networks and advances in control of distributed systems have drawn the attention of many researchers to model various phenomena in social and distributed networks using some mathematical tools such as game theory in order to exploit some of the hidden properties of such networks.
-Such studies not only improve our understanding of the complex nature of social and distributed events, but also enable us to devise more efficient algorithms toward some desired outcomes in such networks.
+With myriads of data from social science and emergence of large scale social and economic networks, studying the evolutionary behavior of complex decision systems has become a major issue in recent years.
+In fact, game theory is one of the strong mathematical tools which has proven quite useful in capturing and modeling the complex nature of human decision making in social and economics networks.
+Despite numerous advances and contributions made in this field of study, there are a lot of barriers and limitations concerning computational issues of different games such as finding Nash equilibrium points or even approximation the equilibrium points of the system.
 
-Due to accelerated growth of economic networks and advances in using game-theoretic tools in various applications, modeling of distributed network storage has become an important issue.
-In general, distributed network storage games or resource allocation games are characterized by a set of agents who compete for the same set of resources \cite{pacifici2012convergence,masucci2014strategic}, and arise in a wide variety of contexts such as congestion games \cite{milchtaich1996congestion,ackermann2008impact,fabrikant2004complexity}, load balancing \cite{ghosh1994dynamic}, peer-to-peer systems \cite{pollatos2008social}, web-caches \cite{gopalakrishnan2012cache}, content management \cite{pollatos2008social}, and market sharing games \cite{goemans2006market}.
-Among many problems that arise in such a context, one that stands out is distributed replication, which not only improves the availability of resources for users, but also increases the reliability of the entire network with respect to customer requests \cite{chun2004selfish}, \cite{goyal2000learning}.
+In this context, we consider in this paper a class of problems known as resource allocation problems.
+In general, resource allocation games are referred to a class of games in which a set of agents or players are competing for the same set of resources and has many applications in various areas such as load balancing, peer-to-peer systems, congestion games, web-caches, content management, and market sharing games among many others \cite{pollatos2008social,pacifici2012convergence,gopalakrishnan2012cache,goemans2006market,masucci2014strategic,ackermann2008impact,fabrikant2004complexity}.
+In fact, one of the important features of such games is to increase the reliability of the entire network with respect to customer needs and to improve the availability of the resources for users.
 
-Distributed replication games with servers that have access to all the resources and are accessible at some cost by users have been studied in \cite{laoutaris2006distributed}.
-Moreover, the uncapacitated selfish replication game where the agents have access to the set of all resources was studied in \cite{chun2004selfish}, where the authors were able to characterize the set of equilibrium points based on the parameters of the problem.
-However, unlike the uncapacitated case, there is no comparable characterization of equilibrium points in capacitated selfish replication games.
-In fact, when the agents have limited capacity, the situation could be much more complicated as the constraint couples the actions of agents much more than in the uncapacitated case or in replication games with servers.
+Typically, resource allocations games can be divided in two general groups: \textit{uncapacitated} and \textit{capacitated}.
+In uncapacitated allocation games the agents can keep even up to all the possible resources in their caches.
+However, there is an associated cost of keeping certain resources in the catch and this eliminates the posibility that every agent keep all the available resources in its catch.
+An instance of such games has been studied in \cite{chun2004selfish}, where the authors were able to fully characterize the set of equilibrium points.
+However, in the capaciteted case the situation could be much more complicated as the constraints on the capacities of the agents couples the actions of agents much more than in the uncapacitated case.
+As a result there is no comparable characterization of equilibrium points in capacitated selfish replication games.
 
-Typically, capacitated selfish replication games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
+In this paper we focus on an instance of capacitated resource allocation games with binary preferences as was introduced in \cite{gopalakrishnan2012cache}, where ``binary preferences" captures the behavioral pattern where players are equally interested in some objects.
+In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
+In fact, CSR games are defined in terms of a set of available resources for each player, where the players are allowed to communicate through an undirected communication graph.
 Such a communication graph identifies the access cost among the players, and the goal for each player is to satisfy his/her customers' needs with minimum cost.
-Ideally, and in order to avoid any additional cost, each player only wants to use his/her own set of resources.
-However, due to limitation on capacity, players do not have access to all the resources and hence, they incur some cost by traveling over the network and borrowing some of the resources which are not available in their own caches from others in order to meet their customers' demands.
-The problem of finding an equilibrium for capacitated selfish replication games in the case of hierarchical networks was studied in \cite{gopalakrishnan2012cache}.
-Moreover, the class of capacitated selfish replication games with binary preferences has been studied in \cite{gopalakrishnan2012cache,etesami2014pure}, where ``binary preferences" captures the behavioral pattern where players are
-equally interested in some objects.
 
-In this paper, we consider the capacitated selfish replication game with binary preferences.
-In this model players act myopically and selfishly, while they are required to fully satisfy their customers' needs.
-Note that, although the players act in a selfish manner with respect to others in satisfying their customer needs, their actions are closely coupled with the others' and they do not have absolute freedom in the selection of their actions.
-It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium.
-This result has been improved in \cite{etesami2014pure} to a linear time algorithm when the number of resources is bounded above by 5.
-However, in general there exist only exponential time algorithms for finding a pure-strategy Nash equilibrium.
-In this work we consider such games over general undirected networks and devise randomize algorithm based on random tree search to find the Nash equilibrium points of the system.
+The problem of finding an equilibrium for CSR games have been studied in \cite{gopalakrishnan2012cache,etesami2014pure}.
+It was shown in \cite{gopalakrishnan2012cache} that when the number of resources is 2, there exists a polynomial time algorithm $\mathcal{O}(n^3)$ to find an equilibrium, where $n$ is the number of players in the game.
+This result has been improved in \cite{etesami2014pure} to a linear time algorithm $\mathcal{O}(n)$ when the number of resources is bounded above by 5.
+Moreover, a quasi-polynomial approximation algorithm $\mathcal{O}(n^{\ln D})$ for approximating any Nash equilibrium of the system within a constant factor has been given in \cite{etesami2015approximation}, where $D$ denotes the diameter of the network.
+In this paper we consider CSR games over general undirected networks and devise a randomized algorithm based on random tree search to find the Nash equilibrium points of the system.
 
 The paper is organized as follows.
-In Section~\ref{sec:game-model}, we introduce capacitated selfish replication games with binary preferences over general undirected networks.
-We review some salient properties of such games and include some relevant existing results on this problem.
-In Section \ref{sec:main-I}, we provide we characterzie the equilibrium points of the system as maximizers of a well-defined function and theroreticaly justify that randomization can be very beneficial for maximizing such function under certain cases.
-Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function and through numerous simulations we show that this method can be quite effective.
+In Section~\ref{sec:game-model}, we introduce CSR games over general undirected networks and review some relevant existing results on this problem.
+In Section \ref{sec:main-I}, we  characterize the equilibrium points of the system as maximizers of a well-defined function and theoretically justify that randomization can be quite beneficial for maximizing such function under certain cases.
+Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function.
+Through numerous simulation results we show that this method can be indeed quite effective.
 We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.
@@
 For a positive integer $n$, we let $[n]:=\{1,2,\ldots,n\}$.
-For a vector $v\in \R^n$, we let $v_i$ be the $i$th entry of $v$.
 We use $\mathcal{G}=([n], \mathcal{E})$ for an undirected underlying network with a node set $\{1,2,\ldots,n\}$ and an edge set $\mathcal{E}$.
 For any two nodes $i, j \in [n]$, we let $d_{\mathcal{G}}(i,j)$ be the graphical distance between them, that is, the length of a shortest path which connects $i$ and $j$.
-The diameter of a graph, denoted by $D$, is the maximum distance between any pair of vertices, that is, $D=\max_{i,j \in [n]} d_{\mathcal{G}}(i,j)$.
-Moreover, for an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
-We denote a specific Nash equilibrium by $P^*$.
-Finally, we use $|S|$ to denote the cardinality of a finite set $S$.
+For an arbitrary node $i\in [n]$ and an integer $r\ge 0$, we define a ball of radius $r$ and center $i$ to be the set of all the nodes in the graph $\mathcal{G}$ whose graphical distance to the node $i$ is at most $r$, i.e., $B_{\mathcal{G}}(i,r)=\{x\in \mathcal{V}| d_{\mathcal{G}}(i,x)\leq r\}$.
+We denote the cardinality of a finite set $A$ by $|A|$.

### 2016-03-10 doc/problem.tex
Modifying Problem Formulation

@@
-\section{Problem Formulation and Existing Results}\label{sec:game-model}
+\section{CSR Game Model}\label{sec:game-model}
 
-In this section we first introduce the capacitated selfish replication game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
-In the balance of this paper, our focus will be on such games, which for simplicity we refer to as CSR games.
+In this section we introduce the capacitated selfish replication (CSR) game with binary preferences as was introduced in \cite{gopalakrishnan2012cache}.
 
-\subsection{CSR Game Model}
-We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$.
-We denote the set of all resources by $O=\{o_1, o_2,\ldots, o_k\}$.
-For simplicity, but without much loss of generality, we assume that each node can hold only one resource in its cache.
-All the results can in fact be extended to CSR games with different capacities (see Remark \ref{rem:varying-cache} below).
-Moreover, we assume that each node has access to all the resources.
-For a particular allocation $P=(P_1, P_2, \ldots, P_n)$, we define the sum cost function $C_i(P)$ of the $i$th player as follows:
+We start with a set of $[n]=\{1,2,\ldots,n\}$ nodes (players) which are connected by an undirected graph $\mathcal{G}=([n], \mathcal{E})$, and a set of all resources denoted by $O=\{o_1, o_2,\ldots, o_k\}$.
+We assume that each node has access to all the resources, but due to the capacity constraint it can hold only one resource in its cache.
+For a particular allocation $P=(P_1, P_2, \ldots, P_n)$ with $P_i\in O$, we define the sum cost function $C_i(P)$ of the $i$th player associated with this  profile as follows:
 \begin{align}\label{eq:CSR-cost-formulation}
@@
 where $\sigma_i(P,o)$ is $i$'s nearest node holding $o$ in $P$.
-Given an allocation profile $P$ we define the {\bf\textit{radius}} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
-Note that if there does not exist such a node, we simply define $r_i(P)=D$, where $D$ is the diameter of the network.
-We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
-In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs and radii for two players $i=1,8$.
+Moreover, we let $\mathcal{P}$ be the set of all possible allocation profiles.
+In Figure \ref{fig:example-model} we have illustrated an instance of the CSR game for $n=11$ and $|O|=3$, and provided the associated costs for two players $i=1,8$.
 
@@
 \begin{remark}
-If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = D + 1, \forall i \in [n]$.
+If some resource $o$ is missing in an allocation profile $P$, we define the cost of each player for that specific resource to be large, e.g., $d_{\mathcal{G}}(i, \sigma_i(P, o)) = n, \forall i \in [n]$.
 Therefore, for $n \ge |O|$, this incentivizes at least one of the players to allocate the missing resources in the network.
@@
 
-\begin{remark}\label{rem:varying-cache}
-Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
-\end{remark}
+%\begin{remark}\label{rem:varying-cache}
+%Actually all the proofs in this paper can be carried over to games with varying capacities by constructing a new network which transfers games with different cache sizes to one with unit size caches \cite{etesami2014pure,gopalakrishnan2012cache}.
+%\end{remark}
 
-\begin{remark}\label{rem:cost-to-radius}
-Given two allocation profiles $P$ and $\tilde{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius, one can easily see that $C_i(P)-C_i(\tilde{P})=r_i(\tilde{P})-r_i(P)$.
-This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
-\end{remark}
+\begin{definition}
+An allocation profile $P^*$ is said to be a pure-strategy Nash equilibrium of the CSR game if 
+\begin{align}\nonumber
+C_i(P^*_i,P^*_{-i})\leq C_i(P_i,P^*_{-i}), \ \forall i\in[n], \forall P_i\in O.
+\end{align}
+where $P^*_{-i}$ denotes the cache content of all the players other than the $i$th player.
+\end{definition}
 
-It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely
+It has been shown in \cite{gopalakrishnan2012cache} that the CSR game has an associated ordinal potential function, and hence, it has at least one pure Nash equilibrium. More precisely:
 
-\smallskip
 \begin{theorem}\label{thm:existence-NE}
@@
 
-Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only gurantee an exponential number of iterations for finding such equilibrium points ($\mathcal{O}(|O|^n)$).
+Although Theorem \ref{thm:existence-NE} proves the existence of NE, however, in general it can only guarantee an exponential number of iterations $\mathcal{O}(|O|^n)$ for finding such equilibrium points.
 Therefore, the main challenge here is to find an efficient way to arrive at an equilibrium which we will address in the remaining of this paper.

### 2016-03-10 doc/motivation.tex
Modifying the Motivation

@@
 Although this function is not monotone along the trajectories of the best response dynamics, however, it is very useful in a sense that it can improve at most linearly many steps because it admits at most linearly many discrete values.
-The explicit form of this function and some of its properties has been given in the following lemma:
+The explicit form of this function and some of its properties has been given in Lemma \ref{lem:NE-characterization}.
+But before we proceed we state the following useful definition.
 
-\smallskip
+\begin{definition}\label{def:radius}
+Given an allocation profile $P$ we define the \textit{radius} of agent $i$, denoted by $r_i(P)$, to be the distance between node $i$ and the nearest node other than her holding the same resource as $i$, i.e., $r_i(P)=\min_{ j\neq i, P_j=P_i}d_{\mathcal{G}}(i,j)$.
+Note that if there does not exist such a node, by convention we define $r_i(P)=n$.
+We suppress the dependence of $r_i(P)$ on $P$ whenever there is no ambiguity.
+\end{definition}
+
 \begin{lemma}\label{lem:NE-characterization}
-Let $r_i$ be the radius of agent $i$ in an allocation profile $P$, and define $M_i(P)$ to be number of different resources in $B_{\mathcal{G}}(i,r_i)$.
-Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an equilibrium of the CSR game.
+For an allocation profile $P$, let $M_i(P)$ be number of different resources in $B_{\mathcal{G}}(i,r_i(P))$.
+Then the function $f(\cdot):\mathcal{P}\rightarrow \mathbbm{R}$ defined by $f(P)=\sum_{i=1}^{n}M_i(P)$ achieves its maximum if and only if $P$ is an Nash equilibrium equilibrium of the CSR game.
 \end{lemma} 
 \begin{proof}
-For an arbitrary equilibrium $P^*$ and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$, we note that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
-In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost (Remark \ref{rem:cost-to-radius}).
+First we note that for any two allocation profiles $P$ and $\bar{P}$ which only differ in the $i$th coordinate, using \eqref{eq:CSR-cost-formulation} and the definition of the radius (Definition \ref{def:radius}), one can easily see that $C_i(P)-C_i(\bar{P})=r_i(\bar{P})-r_i(P)$.
+This establishes an equivalence between decrease in cost and increase in radius for player $i$, when the actions of the other players are fixed.
+Next, let us consider an arbitrary equilibrium $P^*$ profile and a specific node $i$ with equilibrium radius $r^*_i$, i.e., $r^*_i=d_{\mathcal{G}}(i,\sigma_i(P^*,P^*_i))$.
+We claim that all the resources must appear at least once in $B_{\mathcal{G}}(i,r^*_i)$.
+In fact, if a specific resource is missing in $B_{\mathcal{G}}(i,r^*_i)$, then node $i$ can increase its radius by updating its current resource to that specific resource, thereby decreasing its cost.
 But this is in contradiction with $P^*$ being an equilibrium.
 Therefore, for every player $i$ all the resources must appear at least once in $B_{\mathcal{G}}(i,r_i)$, and hence $M_i(P^*)=|O|, \forall i\in [n]$.
-Therefore, $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
-On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure NE, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
-Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius even further.
+This shows that $f(P^*)=n|O|$, which is the maximum possible value that could be taken by $f(\cdot)$ (note that in general we have  $M_i(\cdot)\leq |O|, \forall i$).
+On the other hand, by Theorem \ref{thm:existence-NE} we know that the CSR game always admits a pure-strategy Nash equilibrium, and thus $\max_{P\in \mathcal{P}}f(P)=n|O|$.
+Therefore, if for some allocation profile we have $f(P)=n|O|$, this implies that $M_i(P)=|O|, \forall i\in [n]$, i.e., for every $i\in [n]$, all the resources appear at least once in $B_{\mathcal{G}}(i,r_i)$, which means that $P$ must be an equilibrium since no agent can increase its radius (or equivalently reduce its cost) even further.
 \end{proof}
@@
 \begin{theorem}\label{thm:randomization}
-Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{|O|}$ resources, i.e., $M_i(t)\leq \sqrt{|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
+Given a profile of resources at time $t$, as long as the neighborhood of players are not saturated by more than $\sqrt{d_{min}|O|}$ resources, i.e., $M_i(t)\leq \sqrt{d_{min}|O|}, \forall i$, then there exists a resource such that if a player $i$ updates to that specific resource, the value of function $f$ strictly increases.
 \end{theorem}
@@
 \mathbb{E}[M_i(t+1)]&\ge \frac{M_i(t)}{|O|}+\frac{M_i(t)-1}{|O|}\times 1\cr 
-&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1),
+&\qquad+\frac{|O|-M_i(t)}{|O|}\times (M_i(t)+1)\cr 
+&=1+M_i(t)-\frac{M_i(t)^2+1-M_i(t)}{|O|},
 \end{align}
-where the first term in the above expression is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
+where the first term in the above inequality is the probability that the resource at time $t+1$ remains the same as that at time $t$, the second term is a lower bound for the case where the resource at time $t+1$ changes to one of the different $M_i(t)-1$ resources in $B(i,r_i(t))$, and finally the last term is a lower bound for the case where the resource at node $i$ changes uniformly to one of the possible $|O|-M_i(t)$ which did not appear in $B(i,r_i(t))$.
 
@@
 \mathbb{E}[M_j(t+1)]&\ge \frac{1}{|O|}\times 1+\frac{M_j(t)-1}{|O|}\times M_j(t)\cr 
-&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1),
+&\qquad+\frac{|O|-M_j(t)}{|O|}\times (M_j(t)+1)\cr
+&=\frac{|O|+1-2M_j(t)}{|O|}+M_j(t),
 \end{align}
-where the first term is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second term upper bounds the case where node $i$ updates to one of the possible $M_j(t)-1$ other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term lower bounds the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
+where the first term in the above inequality is a lower bound for the case where node $i$ attains exactly the same resource as node $i$ in the next time step, the second is for the case where node $i$ updates to one of the possible $M_j(t)-1$ resources other than $P_j(t)$ which appeared in $B(j, r_j(t))$, and the last term captures the case where node $i$ changes to one of the possible $|O|-M_j(t)$ which did not appear in $B(j, r_j(t))$.
 Note that for any other node $j$ which is not included in the above two cases we have $M_j(t+1)=M_j(t)$ (since they are not influenced by the random assignment of player $i$).
@@
 &\mathbb{E}[f(t+1)-f(t)]=\mathbb{E}[M_i(t+1)-M_i(t)]\cr 
-&\qquad\qquad\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right)+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\left(\frac{|O|+1-2M_j(t)}{|O|}\right)\cr
-&\qquad\ge 1-\left(\frac{M_i^2+1-M_i}{|O|}\right) >0,
+&\qquad+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\mathbb{E}[M_j(t+1)-M_j(t)]\cr 
+&\ge 1-\frac{M_i^2(t)+1-M_i(t)}{|O|}+\!\!\!\!\!\sum_{j: i\in B(j, r_j(t))}\!\!\!\!\!\frac{|O|+1-2M_j(t)}{|O|}\cr 
+&\ge 1-\frac{M_i^2(t)+1-M_i(t)}{|O|}+d_{min}\frac{|O|+1-2M_j(t)}{|O|}\cr 
+&\ge 1-\frac{d_{min}|O|+1-\sqrt{d_{min}|O|}}{|O|}+d_{min}\frac{|O|+1-2\sqrt{d_{min}|O|}}{|O|}\cr 
+&> 0,
 \end{align}
@@
 Therefore, we have shown that $\mathbbm{E}[f(t+1)-f(t)]>0$ which implies that there exists a resource $o$ such that player $i$ can update to it and strictly improve the value of the function $f(\cdot)$.
-In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$, which takes at most $n|O|^{\frac{3}{2}}$ iterations until the algorithm finds a profile of resources whose objective function $f$ is at least $n\sqrt{|O|}$.
+In fact, such a choice of resource can be exhaustively found by trying all the possible $|O|$ resources for node $i$.
 \end{proof}

### 2016-03-10 doc/algorithm.tex
random tree algorithm

@@
 \section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
+We use random tree search to find the optimum allocation in the CSR game.
+
+%Random tree setup
+
+%Random tree figure
+
+The random tree search algorithm has two phases:
+\begin{enumerate}
+  \item \emph{Warmup Phase:} Similar to other stochastic search algorithms, the runtime for random tree search depends on the choice of the initial allocation profile.
+In order to reduce the variance in search, the random tree starts the search by generating multiple randomized allocation as initial states.
+We emprically observed spending $5\%$ of total samples on finding good initial allocation can substantially reduce overall runtime.
+The random tree stores the 20 best initial allocation (sorted according to our cost function) and ignores the rest.
+  \item \emph{Search Phase:} During the search phase, the random tree picks an allocation from the buffer, changes the resource of one player in the allocation and re-evaluates the radius and number of saturated players in the game.
+If flipping that node improved the allocation, we insert the new allocation back to the buffer, Otherwise we ignore this step and continue.
+\end{enumerate}
+
+%experimental result
+
+We demonstrate the effectiveness and scalability of random tree search using simulation.
+We implemented the random tree search algorithm in C++\footnote{We open-sourced our tools and data and hosted them at \url{github.com/ahmadyan/Capacitated-Selfish-Replication-Game}} and ran our simulation on a Macbook pro laptop equipped with Core-i7 processor and 16gb of memory.
+
+We use a randomly generated Erdos-Renyi graph $G(n,p)$, where $n$ is the number of players and $p$ is the probability of existence of an edge between two player, as a case study.
+We ensured that the graph is connected.
+The CSR game is for $m$ number of resources in the graph $G$.
+We executed the random tree search algorithm to find the optimal allocation.
+The random tree would terminate when the cost function reaches it's maximum at $n\times m$.
+To ensure correctness, we assert the number of unsaturated neighborhoods in the graph $G$ to be zero at termination.
+
+Table \ref{tab:result1} shows the result of the random tree search algorithm for different case studies. Our algorithm quickly found the equilibrium point in all of our experiments.
+
+\begin{table}[]
+\centering
+\caption{Random tree search profile for different random graphs}
+\label{tab:result1}
+\begin{tabular}{lllll}
+n   & p    & m  & iterations & time (s) \\
+100 & 0.05 & 5  & 1453       & x        \\
+100 & 0.05 & 20 & 6028       & x        \\
+20  & 0.05 & 3  & 560        & x        \\
+20  & 0.5  & 10 & 1045       & x
+\end{tabular}
+\end{table}

### 2016-03-10 src/main.cpp

@@ -7,11 +7,11 @@ using namespace std;
 
 int main(int argc, const char * argv[]) {
 	Graph* g = new Graph();
-	int playerSize = 100;
-	int graphConnectivityFactor = 2;
+	int playerSize = 20;
+	int graphConnectivityFactor = 3 ;
 	int resourceSize = 10;
 	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
-	g->generateErdosRenyiRandomGraph(playerSize, 0.05);
+	g->generateErdosRenyiRandomGraph(playerSize, 0.4);
     Search* search = new Search(playerSize, resourceSize, g);
     //search->run();
     search->run();

### 2016-03-10 doc/introduction.tex
fixed conflicts

@@
 
+We use random tree search algorithm to locate Nash equilibrium points in CSR game.
+The random tree search algorithm is an efficient randomized algorithm for searching the state space of games.
+The random tree algorithm works by sampling the allocation space of the CSR game.
+The algorithm searches for the optimum allocation, resulting in the Nash equilibrium.
+The random tree search is guided by maximizing a cost function associated with each allocation.
+The random tree grows multiple tree walks from an initial allocation.
+The random tree branches the simulation walks to bias the walk toward the optimim allocation and avoiding the local minimas.
+Recently, stochastic random tree-based search methods have emerged as an alternative to classic optimization algorithms.
+The random tree algorithm has been used to optimize analog circuits \cite{adel2015}, robotic motion planning \cite{Lavalle2006}, and deep learning\cite{silver2016}.
+In comparison to the classic optimization algorithms such as simulated annealing or hill climbing, the random tree search is more efficient and does not get stuck in local minimas \cite{adel15, Lavalle2006}.
+
 The paper is organized as follows.
@@
 Following this, in Section \ref{sec:apx-alg} we device a random tree search algorithm for maximize the objective function.
-Through numerous simulation results we show that this method can be indeed quite effective.
+Through numerous simulation results we show that this method can be indeed quite effective on large scale graphs in practical settings.
 We conclude the paper with identifying future directions of research in Section~\ref{sec:conclusion}.

### 2016-03-12 src/main.cpp
added boost accumulator to compute mean of iterations

@@ -1,22 +1,43 @@
 #include <iostream>
+#include <boost/accumulators/accumulators.hpp>
+#include <boost/accumulators/statistics/stats.hpp>
+#include <boost/accumulators/statistics/variance.hpp>
+#include <boost/accumulators/statistics/count.hpp>
+#include <boost/accumulators/statistics/mean.hpp>
+#include <boost/accumulators/statistics/moment.hpp>
 #include "graph.h"
 #include "profile.h"
 #include "search.h"
 
 using namespace std;
+using namespace  boost::accumulators;
 
 int main(int argc, const char * argv[]) {
-	Graph* g = new Graph();
+    accumulator_set<double, stats<tag::variance> > acc;
+    accumulator_set<double, stats<tag::variance> > acc2;
+    int runs=10;
+
 	int playerSize = 20;
 	int graphConnectivityFactor = 3 ;
 	int resourceSize = 10;
-	//g->generateRandomGraph(playerSize, graphConnectivityFactor);
-	g->generateErdosRenyiRandomGraph(playerSize, 0.4);
-    Search* search = new Search(playerSize, resourceSize, g);
-    //search->run();
-    search->run();
-    delete search;
-    delete g;
+    for(int i=0;i<runs;i++){
+        Graph* g = new Graph();
+        //g->generateRandomGraph(playerSize, graphConnectivityFactor);
+        g->generateErdosRenyiRandomGraph(playerSize, 0.4);
+        Search* search = new Search(playerSize, resourceSize, g);
+        //search->run();
+        search->run();
+        acc(search->getStat());
+        delete search;
+        delete g;
+        
+    }
+    
+    cout << "Count : " << boost::accumulators::count(acc) << endl;
+    cout<< "Mean  :  "<< mean(acc) << endl;
+    //cout<<"moment : "<<moment<2>(acc)<<endl;
+    cout<<"deviation : "<< sqrt(variance(acc)) << endl;
+
     
     system("PAUSE");
     return 0;

### 2016-03-12 src/profile.cpp

@@ -8,6 +8,7 @@
 #include <set>
 #include <list>
 #include <cstdint>
+#include <cmath>
 #include <numeric>
 
 Profile::Profile(int s, int r){
@@ -183,7 +184,8 @@ int Profile::updateRadius(Node* v){
 int Profile::objectiveSum(Graph* g){
 	int result = 0;
 	for (int i = 0; i < size; i++){
-		result += objective(g->nodes[i]);
+        auto obj = objective(g->nodes[i]);
+        result += obj; //(obj * log(obj));
 	}
     cost=result;
 	return result;

### 2016-03-12 src/search.cpp

@@ -23,6 +23,7 @@ Search::Search(int ps, int rs, Graph* gg){
     g=gg;
     buffersize=10;
     buffer = Container(pq);
+    iterations=0;
 }
 
 Search::~Search(){
@@ -69,6 +70,7 @@ void Search::run(){
 
             for(int i=0;i<buffersize;i++)
                 cout << get(i)->cost << endl ;
+            iterations=i;
             return;
         }
     }
@@ -96,4 +98,8 @@ Profile* Search::get(int i){
 
 Profile* Search::sample(){
     return buffer[rand()%buffer.size()];
+}
+
+int Search::getStat(){
+    return iterations;
 }

### 2016-03-12 src/search.h

@@ -13,7 +13,7 @@ class Search{
     int playerSize;
     int resourceSize;
     Graph* g;
-    
+    int iterations;
     int buffersize;
     //priority_queue<int, vector<int>, less<int> > pq;
     //vector<int> buffer;
@@ -29,4 +29,5 @@ public:
     void push(Profile*);
     Profile* sample();
     Profile* get(int);
+    int getStat();
 };

### 2016-03-13 src/main.cpp
added time measurement for evaluating runs

@@ -5,6 +5,7 @@
 #include <boost/accumulators/statistics/count.hpp>
 #include <boost/accumulators/statistics/mean.hpp>
 #include <boost/accumulators/statistics/moment.hpp>
+#include <chrono>
 #include "graph.h"
 #include "profile.h"
 #include "search.h"
@@ -20,25 +21,26 @@ int main(int argc, const char * argv[]) {
 	int playerSize = 20;
 	int graphConnectivityFactor = 3 ;
 	int resourceSize = 10;
+    std::chrono::milliseconds duration;
+    duration.zero();
     for(int i=0;i<runs;i++){
         Graph* g = new Graph();
         //g->generateRandomGraph(playerSize, graphConnectivityFactor);
         g->generateErdosRenyiRandomGraph(playerSize, 0.4);
         Search* search = new Search(playerSize, resourceSize, g);
-        //search->run();
+        auto start = std::chrono::system_clock::now();
         search->run();
+        duration += std::chrono::duration_cast<std::chrono::milliseconds>(std::chrono::system_clock::now() - start);
         acc(search->getStat());
         delete search;
         delete g;
-        
     }
-    
-    cout << "Count : " << boost::accumulators::count(acc) << endl;
-    cout<< "Mean  :  "<< mean(acc) << endl;
+    duration /= runs;
+    cout << " Average simulation time = " << duration.count() << "ms" << endl ;
+    cout << " Count : " << boost::accumulators::count(acc) << endl;
+    cout<< " Mean  :  "<< mean(acc) << endl;
     //cout<<"moment : "<<moment<2>(acc)<<endl;
-    cout<<"deviation : "<< sqrt(variance(acc)) << endl;
-
-    
+    cout<<" deviation : "<< sqrt(variance(acc)) << endl;
     system("PAUSE");
     return 0;
 }

### 2016-03-13 src/search.cpp

@@ -51,15 +51,12 @@ void Search::run(){
         //int c0 = p->computeCost(g->nodes[g->nodes.size() - 1]);
         p->updateRadius(g);
         int s = p->updateSaturation(g);
-
-
-
         int o = p->objectiveSum(g);
 
         if (o>max) max = o ;
         db.push_back(p);
         push(p);
-        cout << i << ", " << s << ", " << o<< endl ;
+        //cout << i << ", " << s << ", " << o<< endl ;
         //p->flip(g, g->nodes[i%playerSize]);
         //p->updateRadius(g);
         //cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
@@ -68,8 +65,8 @@ void Search::run(){
             cout << " Maximum Objective= " << max << endl;
             cout << " Buffer ----------- " << endl ;
 
-            for(int i=0;i<buffersize;i++)
-                cout << get(i)->cost << endl ;
+            //for(int i=0;i<buffersize;i++)
+            //    cout << get(i)->cost << endl ;
             iterations=i;
             return;
         }

### 2016-03-13 src/main.cpp
implemented greedypick for next player

@@ -16,9 +16,9 @@ using namespace  boost::accumulators;
 int main(int argc, const char * argv[]) {
     accumulator_set<double, stats<tag::variance> > acc;
     accumulator_set<double, stats<tag::variance> > acc2;
-    int runs=10;
+    int runs=1;
 
-	int playerSize = 20;
+	int playerSize = 100;
 	int graphConnectivityFactor = 3 ;
 	int resourceSize = 10;
     std::chrono::milliseconds duration;
@@ -26,7 +26,7 @@ int main(int argc, const char * argv[]) {
     for(int i=0;i<runs;i++){
         Graph* g = new Graph();
         //g->generateRandomGraph(playerSize, graphConnectivityFactor);
-        g->generateErdosRenyiRandomGraph(playerSize, 0.4);
+        g->generateErdosRenyiRandomGraph(playerSize, 0.05);
         Search* search = new Search(playerSize, resourceSize, g);
         auto start = std::chrono::system_clock::now();
         search->run();

### 2016-03-13 src/profile.cpp

@@ -89,8 +89,8 @@ int Profile::updateSaturation(Graph* g){
         saturation[i] = updateSaturation(g->nodes[i]);
         if(saturation[i]!=resources){
             unsaturatedNeighbors++;
+            unsatisfiedPlayers.push_back(i);
          //   std::cout << "* " << saturation[i] << " " << resources << std::endl ;
-
         }
         
         //if(saturation[i]<=sqrt(resources))
@@ -298,4 +298,10 @@ void Profile::flip(Graph* g, Node* v){
     allocation[v->id] = uint_dist(rng)%resources;
     updateRadius(g);
     updateSaturation(g);
+}
+
+int Profile::sampleUnsatisfiedPlayer(){
+    if(unsatisfiedPlayers.size()==0) return -1;// throw Exception("unsatisfiedPlayer size is 0");
+    int i = rand()%unsatisfiedPlayers.size();
+    return unsatisfiedPlayers[i];
 }

### 2016-03-13 src/profile.h

@@ -17,6 +17,8 @@ public:
 	std::vector<int> radius;
     //determines the number of resources around the neighborhood of size radius(i) of each node i
     std::vector<int> saturation;
+    //list of all the players that have unsatisfied neighbors in this allocation
+    std::vector<int> unsatisfiedPlayers;
     int cost;
     
     std::mt19937 rng;
@@ -38,6 +40,7 @@ public:
     int updateSaturation(Node* v);
     
     void flip(Graph* g, Node* v);
+    int sampleUnsatisfiedPlayer();
 };
 
 

### 2016-03-13 src/search.cpp

@@ -44,7 +44,13 @@ void Search::run(){
             p = new Profile(q);
             for(int j=0;j<1+0.1*total_iteration/i; j++){
                 //p->generateRandomProfile();
-                p->flip(g, g->nodes[rand()%playerSize]);
+                if(rand()%100 < 5){
+                    //let the algorithm intentionally make mistakes
+                    p->flip(g, g->nodes[rand()%playerSize]);
+                }else{
+                    //choose the next player in a greedy fashion
+                    p->flip(g, g->nodes[q->sampleUnsatisfiedPlayer()]);
+                }
             }
         }
 
@@ -56,7 +62,7 @@ void Search::run(){
         if (o>max) max = o ;
         db.push_back(p);
         push(p);
-        //cout << i << ", " << s << ", " << o<< endl ;
+        cout << i << ", " << s << ", " << o<< endl ;
         //p->flip(g, g->nodes[i%playerSize]);
         //p->updateRadius(g);
         //cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;

### 2016-03-14 doc/algorithm.tex
updating the algorithm section in the document

--- 2016-03-02 doc/algorithm.tex
@@
 \section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
+We use random tree search to find the optimum allocation in the CSR game.
+The search algorithm starts by randomly generating a few allocation as seeds.
+At each iteration, we pick a sampled allocation (from a buffer) and improve its score by randomly changing a resource of some player in the game.
+Over time, we save the best allocations we have seen so far in a buffer.
+Eventually the algorithm will converge to the optimal allocation in the game.
+
+%n=number of players
+%k=number of resources
+%q=size of priority-queue
+
+%Random tree setup
+Each node in the random tree is $n$-dimensional vector denoting an allocation instance.
+During simulation, we keep track of the best nodes (allocations) sampled so far, sorted by the score function, in a priority queue of size $q$.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{random-tree-figure-1}
+\end{center}
+\caption{Random tree with 6 sampled allocations ${\bf p}_0\dots {\bf p}_5$. Allocations are sorted in a priority queue of a a fixed size according to their score.}
+\label{fig:random_tree_1}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{random-tree-figure-2}
+\end{center}
+\caption{After updating allocation ${\bf p}_3$, we find a new high-scoring allocation ${\bf p}_*$.
+Pushing ${\bf p}_*$ to the top of the queue evicts the least-scoring allocation ${\bf p}_0$.
+As a result, we will no longer branch the simulation from ${\bf p}_0$.
+}
+\label{fig:random_tree_2}
+\end{figure}
+
+The random tree search algorithm has two phases:
+\begin{enumerate}
+  \item \emph{Warmup Phase:} Similar to other stochastic search algorithms, the runtime for random tree search depends on the choice of the initial allocation profile.
+In order to reduce the variance in search, the random tree starts the search by generating multiple randomized allocation as initial states.
+We emprically observed spending $5\%$ of total samples on finding good initial allocation can substantially reduce overall runtime.
+The random tree stores the 20 best initial allocation (sorted according to our cost function) and ignores the rest.
+  \item \emph{Search Phase:} During the search phase, the random tree picks an allocation from the buffer, changes the resource of one player in the allocation and re-evaluates the radius and number of saturated players in the game.
+If flipping that node improved the allocation, we insert the new allocation back to the buffer, Otherwise we ignore this step and continue.
+\end{enumerate}
+
+The random tree search algorithm work as follows.
+Initially, we generate a few random allocation as seends and compute the score of each allocation.
+Then we push these initial seeds into the fixed-size priority queue sorted by each allocation's score.
+The froniter set is the set of the $n$ highest scoring allocation that we found so far.
+At each iteration, the random tree algorithm pick an allocation from the frontier set, and changes a resource of one of the unsatisfied players.
+Then the random tree updates the score function and pushes back the new allocation into the frontier set.
+If the new allocation has a better score than the lowest-scoring allocation in the frontier set, we drop the least-score element from the frontier set.
+As a result, the frontier set always has a fixed-size.
+
+\paragraph{Complexity Analysis:}
+In order to understand the computational complexity of the random tree search algorithm, we break-down the computation at every iteration.
+Each iteration in the random tree search consists of three actions:
+i) Picking a node from the frontier set (the priority queue) and changing the allocation,
+ii) Updating the raidus and saturation of the new allocation, and
+iii) Pushing back the new node back to the priority queue.
+The computational complexity of the first part is $O(1)$.
+The most expensive part of the algorithm is updating the radius and saturation of each player, which requires running a breath-first search in the player graph.
+The computational complexity of running BFS is O(V+E) where $V$ is the number of the players and $E$ is the number of the edges in the CSR graph.
+Finally, the computational complexity of inserting the new allocation back to the priority queue is $O(log n)$, where $n$ is the size of the fixed priority queue.
+Finally, we keep the priority queue sorted in order to make weighted sampling, as a result, the complexity of inserting into the priority queue is $O(log(n)\times log(log(n)))$.
+The overal complexity of the algorithm is $O(V\times(V+E)\times log(n)\times \log\log(n))$.
+
+The random tree search algorithm is probabilistically complete \cite{Lavalle2006}.
+Therefore, given enought time it will always find the optimal allocation.
+However, there is no bound on the number of sufficient iterations for finding the optimal allocation.
+We emprically demonstrate the random tree requires a very few iteration to find the equilibrium points even for very large scale graphs.

### 2016-03-14 doc/experiments.tex
updating the algorithm section in the document

\section{Experimental Results and Discussions}\label{sec:results}
We demonstrate the effectiveness and scalability of random tree search using simulation.
We implemented the random tree search algorithm in C++\footnote{Our tools and data are open-source. Our repository can be accessed at \url{github.com/ahmadyan/Capacitated-Selfish-Replication-Game}} and ran our simulation on a Macbook pro laptop equipped with Core-i7 processor and 16GB of memory.

For case-studies, we use a randomly generated Erdos-Renyi graph $G(n,p)$, where $n$ is the number of players and $p$ is the probability of existence of an edge between two player. We ensured that the graph is connected. The CSR game is for $m$ number of resources in the graph $G$. We executed the random tree search algorithm to find the optimal allocation. The random tree would terminate when the cost function reaches it's maximum at $n\times m$. For each entry point, we repeat the experiments 100 times and reported the mean number of iterations and execition time. To ensure correctness, we checked the number of unsaturated neighborhoods in the graph $G$ to be zero at termination.

Table \ref{tab:result1} shows the result of the random tree search algorithm for different games.
Our algorithm quickly found the equilibrium point in all of our experiments.

\begin{table}[]
\centering
\caption{Random tree search profile for different random graphs}
\label{tab:result1}
\begin{tabular}{lllll}
n   & p    & m  & iterations & time (s) \\
100 & 0.05 & 5  & 1453       & x        \\
100 & 0.05 & 20 & 6028       & x        \\
20  & 0.05 & 3  & 560        & x        \\
20  & 0.5  & 10 & 1045       & x
\end{tabular}
\end{table}

% two types of results:
% 1. Showing algorithm w.r.t. Number of iterations--> should be linear
% 2. Algorithm w.r.t. its runtime --> O(n^2)

### 2016-03-14 src/main.cpp

@@ -16,8 +16,7 @@ using namespace  boost::accumulators;
 int main(int argc, const char * argv[]) {
     accumulator_set<double, stats<tag::variance> > acc;
     accumulator_set<double, stats<tag::variance> > acc2;
-    int runs=1;
-
+    int runs=10;
 	int playerSize = 100;
 	int graphConnectivityFactor = 3 ;
 	int resourceSize = 10;

### 2016-03-14 src/profile.cpp

@@ -296,12 +296,28 @@ int Profile::computeCost(Node* v){
 void Profile::flip(Graph* g, Node* v){
     std::uniform_int_distribution<uint32_t> uint_dist;
     allocation[v->id] = uint_dist(rng)%resources;
-    updateRadius(g);
-    updateSaturation(g);
+    //update(g);
+}
+
+void Profile::flip(Graph* g, std::vector<int> unsat){
+    std::uniform_int_distribution<uint32_t> uint_dist;
+    for(int i=0;i<unsat.size();i++){
+        allocation[unsat[i]] = uint_dist(rng)%resources;
+    }
+    //update(g);
 }
 
 int Profile::sampleUnsatisfiedPlayer(){
     if(unsatisfiedPlayers.size()==0) return -1;// throw Exception("unsatisfiedPlayer size is 0");
     int i = rand()%unsatisfiedPlayers.size();
     return unsatisfiedPlayers[i];
+}
+
+std::vector<int> Profile::getUnsatisfiedPlayers(){
+    return unsatisfiedPlayers;
+}
+
+void Profile::update(Graph* g){
+    updateRadius(g);
+    updateSaturation(g);
 }

### 2016-03-14 src/profile.h

@@ -35,12 +35,13 @@ public:
 	int updateRadius(Node* v);
 	int objective(Node* v);
 	int objectiveSum(Graph* g);
-    
     int updateSaturation(Graph* g);
     int updateSaturation(Node* v);
-    
     void flip(Graph* g, Node* v);
+    void flip(Graph* g, std::vector<int> unsat);
     int sampleUnsatisfiedPlayer();
+    std::vector<int> getUnsatisfiedPlayers();
+    void update(Graph* g);
 };
 
 

### 2016-03-14 src/search.cpp

@@ -31,10 +31,14 @@ Search::~Search(){
 
 void Search::run(){
     int max = -1;
+    double flipping_factor = 0.1;
+    int error_probability = 5; // %100
     int total_iteration = 10000;
-    int warmupPhase=total_iteration/20;
+    int numberOfFlips = 0;
+    int warmupPhase = playerSize; //total_iteration/20;
+
     for (int i = 0; i < total_iteration; i++){
-        buffersize = 20 + log(i);
+        buffersize = 10;//+(int)sqrt(i);
         Profile* p;
         if(i<warmupPhase){
             p = new Profile(playerSize, resourceSize);
@@ -42,9 +46,15 @@ void Search::run(){
         }else{
             Profile* q = sample();
             p = new Profile(q);
-            for(int j=0;j<1+0.1*total_iteration/i; j++){
+            //flip all of the unsatisfied nodes
+            //p->flip(g, q->getUnsatisfiedPlayers());
+            numberOfFlips = 1+rand()%(q->getUnsatisfiedPlayers().size()-1);
+            //for(int j=0;j<1+flipping_factor*total_iteration/i; j++){
+            for(int j=0;j<numberOfFlips; j++){
+               // cout << j << endl ;
+
                 //p->generateRandomProfile();
-                if(rand()%100 < 5){
+                if(rand()%100 < error_probability){
                     //let the algorithm intentionally make mistakes
                     p->flip(g, g->nodes[rand()%playerSize]);
                 }else{
@@ -52,6 +62,7 @@ void Search::run(){
                     p->flip(g, g->nodes[q->sampleUnsatisfiedPlayer()]);
                 }
             }
+            p->update(g);
         }
 
         //int c0 = p->computeCost(g->nodes[g->nodes.size() - 1]);
@@ -62,7 +73,7 @@ void Search::run(){
         if (o>max) max = o ;
         db.push_back(p);
         push(p);
-        cout << i << ", " << s << ", " << o<< endl ;
+        cout << i << ", " << s << ", " << o << " " << numberOfFlips << endl ;
         //p->flip(g, g->nodes[i%playerSize]);
         //p->updateRadius(g);
         //cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
@@ -78,8 +89,6 @@ void Search::run(){
         }
     }
     cout << "Maximum Objective= " << max << endl;
-    
-
 }
 
 void Search::push(Profile* new_elem){
[…]

### 2016-03-15 src/graph.cpp
running few simulations, committing the results

@@ -17,10 +17,8 @@ Graph::~Graph(){
     }
 }
 
-//very simple random graph generator
 //incrementally constructs the graph, vertex by vertex
-//randomly connects the new vertex to at least p other vertices (no guarantees for the first p-vertices)
-//todo: replace this with Erdos random graphs
+//randomly connects  vertex to at least p other vertices
 void Graph::generateRandomGraph(int size, int p){
     std::mt19937 rng;
     std::array<int, 624> seed_data;
@@ -32,14 +30,14 @@ void Graph::generateRandomGraph(int size, int p){
     
     for(int i=0;i<size;i++){
         Node* v = new Node(i);
-        int j=0;
-        while(j<std::min(i,p)){
-            auto u = uint_dist(rng)%i;
-            if(v->addEdge(nodes[u])){
-                j++;
-            }
-        }
         nodes.push_back(v);
+    }
+    for(int i=0;i<size;i++){
+        if(i>0) nodes[i]->addEdge(nodes[i-1]);  //to ensure connectedness
+        for(int j=0;j<p-1;j++){
+            auto u = uint_dist(rng)%size;
+            nodes[i]->addEdge(nodes[u]);
+        }
     }
 }
 

### 2016-03-15 src/main.cpp

@@ -20,12 +20,16 @@ int main(int argc, const char * argv[]) {
 	int playerSize = 100;
 	int graphConnectivityFactor = 3 ;
 	int resourceSize = 10;
+    double edgeProbability = 0.19;
     std::chrono::milliseconds duration;
     duration.zero();
     for(int i=0;i<runs;i++){
+        double completionPercent = (100.0*i)/runs;
+        cout << " Iteration " << i <<  " ," << completionPercent << "% completed." << endl ;
         Graph* g = new Graph();
         //g->generateRandomGraph(playerSize, graphConnectivityFactor);
-        g->generateErdosRenyiRandomGraph(playerSize, 0.05);
+        g->generateErdosRenyiRandomGraph(playerSize, edgeProbability);
+        //cout << g->toString() << endl ;
         Search* search = new Search(playerSize, resourceSize, g);
         auto start = std::chrono::system_clock::now();
         search->run();

### 2016-03-15 src/profile.cpp

@@ -76,23 +76,39 @@ void Profile::generateRandomProfile(){
 
 std::string Profile::toString(){
     std::stringstream ss;
+    ss << "Cost=" << cost << std::endl ;
+    ss << "Allocation= ";
     for(int i=0;i<size;i++){
         ss << allocation[i] << ", " ;
+    }
+    ss << std::endl;
+    ss << "Radius= ";
+    for(int i=0;i<size;i++){
+        ss << radius[i] << ", " ;
+    }
+    ss << std::endl;
+    ss << "Saturation= ";
+    for(int i=0;i<size;i++){
+        ss << saturation[i] << ", " ;
+    }
+    ss << std::endl;
+    ss << "Unsatisfied Players= ";
+    for(int i=0;i<unsatisfiedPlayers.size();i++){
+        ss << unsatisfiedPlayers[i] << ", " ;
     }
     ss << std::endl;
     return ss.str();
 }
 
 int Profile::updateSaturation(Graph* g){
+    unsatisfiedPlayers.clear();
     auto unsaturatedNeighbors=0;
     for (auto i = 0; i < size; i++){
         saturation[i] = updateSaturation(g->nodes[i]);
         if(saturation[i]!=resources){
             unsaturatedNeighbors++;
             unsatisfiedPlayers.push_back(i);
-         //   std::cout << "* " << saturation[i] << " " << resources << std::endl ;
         }
-        
         //if(saturation[i]<=sqrt(resources))
         //    unsaturatedNeighbors++;
     }

### 2016-03-15 src/search.cpp

@@ -48,11 +48,11 @@ void Search::run(){
             p = new Profile(q);
             //flip all of the unsatisfied nodes
             //p->flip(g, q->getUnsatisfiedPlayers());
-            numberOfFlips = 1+rand()%(q->getUnsatisfiedPlayers().size()-1);
+            int denom = q->getUnsatisfiedPlayers().size()-1;
+            denom = denom==0?1:denom;
+            numberOfFlips = 1+rand()%(denom);
             //for(int j=0;j<1+flipping_factor*total_iteration/i; j++){
             for(int j=0;j<numberOfFlips; j++){
-               // cout << j << endl ;
-
                 //p->generateRandomProfile();
                 if(rand()%100 < error_probability){
                     //let the algorithm intentionally make mistakes
@@ -64,29 +64,28 @@ void Search::run(){
             }
             p->update(g);
         }
-
-        //int c0 = p->computeCost(g->nodes[g->nodes.size() - 1]);
         p->updateRadius(g);
         int s = p->updateSaturation(g);
         int o = p->objectiveSum(g);
-
         if (o>max) max = o ;
         db.push_back(p);
         push(p);
-        cout << i << ", " << s << ", " << o << " " << numberOfFlips << endl ;
+        //cout << i << ", " << s << ", " << o << " " << numberOfFlips << endl ;
         //p->flip(g, g->nodes[i%playerSize]);
         //p->updateRadius(g);
         //cout << " unsaturated neighbors = " << p->updateSaturation(g) << " " << "cost=" ;
         if(o==playerSize*resourceSize){
+            //cout << p->toString() << endl ;
             cout << " Found equilibrium point after " << i << " iterations" << endl ;
             cout << " Maximum Objective= " << max << endl;
             cout << " Buffer ----------- " << endl ;
 
             //for(int i=0;i<buffersize;i++)
             //    cout << get(i)->cost << endl ;
-            iterations=i;
+
             return;
         }
+        iterations=i;
     }
     cout << "Maximum Objective= " << max << endl;
 }
@@ -123,4 +122,16 @@ Profile* Search::sample(){
 
 int Search::getStat(){
     return iterations;
+}
+
+//buggy code,
+//sort does not uses profile's < operator to sort according to cost
+string Search::getOptimalAllocation(){
+    std::sort(buffer.begin(), buffer.end());
+    for(int i=0;i<buffer.size();i++){
+        cout << buffer[i]->toString() << endl ;
+
+    }
+    auto best = buffer[0];
+    return best->toString();
 }

### 2016-03-15 src/search.h

@@ -19,7 +19,6 @@ class Search{
     //vector<int> buffer;
     priority_queue<Profile*, vector<Profile*>, profileGreaterComparator > pq;
     vector<Profile*> buffer;
-    
     vector<Profile*> db;
 public:
     
@@ -30,4 +29,5 @@ public:
     Profile* sample();
     Profile* get(int);
     int getStat();
+    string getOptimalAllocation();
 };

### 2016-03-15 doc/algorithm.tex
updated tex file

--- 2016-03-02 doc/algorithm.tex
@@
 \section{Random Tree Search Algorithm for Finding NE}\label{sec:apx-alg}
+We use random tree search algorithm to find the optimum resource allocation in the CSR game.
+Each node in the random tree is $n$-dimensional vector denoting an allocation instance.
+The search algorithm adds new nodes to the tree by sampling new allocations and optimizing the cost of each allocation iteratively.
+The search algorithm starts by randomly generating a few allocation as seeds and stores them in a buffer.
+This buffer maintains the highest scoring allocations that we have found so far.
+Next, at each iteration, the search algorithm picks an allocation from the buffer.
+The algorithm improves the score of the allocation by randomly changing a resource of an unsatisfied player in the allocation. Next, we push back the updated allocation back into the buffer.
+By iteratively uptimizing allocations, the search algorithm eventually converges toward the optimal allocation in the game.
+
+%n=number of players
+%k=number of resources
+%q=size of priority-queue
+%p=probabiliy of existence of an edge between two player
+% b = size of priority-queue
+
+Figure~\ref{fig:random_tree_1} shows the random tree and the buffer.
+Each edge between two nodes ${\bf p}_i$ and ${\bf p}_j$ in the random tree denotes the search algorithm found allocation ${\bf p}_j$ by chaning resources of a few players in allocation ${\bf p}_i$.
+The buffer is a fixed-size priority queue that sorts the allocations according to their score.
+Figure~\ref{fig:random_tree_1} shows the progress of search algorithm during one iteration.
+At every iteration, we randomly pick an allocation from the buffer, say ${\bf p}_3$.
+We compute the new allocation ${\bf p}_*$ by changing the resources of the unsatisfied players in allocation ${\bf p}_3$.
+Next, we compute the radius and saturation of each player in the new allocation ${\bf p}_*$ in order to compute the ${\bf p}_*$'s score.
+Finally, we insert the new allocation ${\bf p}_*$ into the buffer according to it's score.
+The buffer is sorted and implemented using a priority queue.
+If the ${\bf p}_*$ has a better score than the least-scoring allocation in the buffer, in this case ${\bf p}_0$, ${\bf p}_*$ will be pushed to the queue and ${\bf p}_0$ will be evicted.
+If ${\bf p}_*$ is scoring less than ${\bf p}_*$ we discard the new allocation and continue the search.
+The algorithm will terminate when we find an allocation that satisfied all players.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{random-tree-figure-1}
+\end{center}
+\caption{Random tree with 6 sampled allocations ${\bf p}_0\dots {\bf p}_5$. Allocations are sorted in a priority queue of a a fixed size according to their score.}
+\label{fig:random_tree_1}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{random-tree-figure-2}
+\end{center}
+\caption{After updating allocation ${\bf p}_3$, we find a new high-scoring allocation ${\bf p}_*$.
+Pushing ${\bf p}_*$ to the top of the queue evicts the least-scoring allocation ${\bf p}_0$.
+As a result, we will no longer branch the simulation from ${\bf p}_0$.
+}
+\label{fig:random_tree_2}
+\end{figure}
+
+We utilize many heuristics to improve performance of the random tree search algorithm. We will describe these heuristics in more details.
+
+\paragraph{Warmup phase:} Similar to other stochastic search algorithms, the runtime for random tree search depends on the choice of the initial allocation profile.
+In order to reduce the variance in search, the random tree starts the search by generating multiple randomized allocation as initial seeds.
+We emprically observed using $n$ (the number of players) iterations in the warmpup phase can substantially reduce overall runtime.
+In the end of warmpup phase, we sort the seeds according to their score and only keep the $b$ best seeds that we found, where $b$ is the size of the buffer.
+
+\paragraph{Buffer size:} The buffer size $b$ has has a deep impact on how the random tree searches the allocation space.
+If we choose a very small buffer size, $b=1$, the random tree search becomes a greedy random walk in the space.
+As a result, the algorithm's performance will degrade and it can get stuck in local minimas.
+On the other hand,
+We emprically observed setting the buffer size at a fixed size 10 yields the optimal performance.
+
+\paragraph{Updating allocations:} At every iteration, we have to make a choice of which player's resource to update in the allocation.
+The random tree algorithm updates the resources of a few of unsatisfied players in the allocation.
+If we update a very few players, say 1 or 2, the algorithm converges slowly.
+On the other hand, if we update too many players, specially at the begining, the algorithm is unable to efficiently optimize each allocation.
+We updates an expected half of the players at each iteration.
+Furthermore, with a low probability ($5\%$), we will update a player at random (that might even be a satisfied player).
+These type of intentionally adding error, althought seems counter-intuitive, is shown to be very effective and practical in randomized search algorithms.
+
+%The random tree search algorithm work as follows.
+%Initially, we generate a few random allocation as seends and compute the score of each allocation.
+Then we push these initial seeds into the fixed-size priority queue sorted by each allocation's score.
+The froniter set is the set of the $n$ highest scoring allocation that we found so far.
+%At each iteration, the random tree algorithm pick an allocation from the frontier set, and changes a resource of one of the unsatisfied players.
+Then the random tree updates the score function and pushes back the new allocation into the frontier set.
+%If the new allocation has a better score than the lowest-scoring allocation in the frontier set, we drop the least-score element from the frontier set.
+As a result, the frontier set always has a fixed-size.
+
+\paragraph{Complexity Analysis:}
+In order to understand the computational complexity of the random tree search algorithm, we break-down the computation at every iteration.
+Each iteration in the random tree search consists of three actions:
+i) Picking a node from the frontier set (the priority queue) and changing the allocation,
+ii) Updating the raidus and saturation of the new allocation, and
+iii) Pushing back the new node back to the priority queue.
+The computational complexity of the first part is $O(1)$.
+The most expensive part of the algorithm is updating the radius and saturation of each player, which requires running a breath-first search in the player graph.
+The computational complexity of running BFS is $O(n+e)$ where $n$ is the number of the players and $e$ is the number of the edges in the CSR graph.
+Finally, the computational complexity of inserting the new allocation back to the priority queue is $O(log b)$, where $b$ is the buffer size.
+Finally, we keep the priority queue sorted in order to make weighted sampling, as a result, the complexity of inserting into the priority queue is $O(b\log^2(b))$.
+The overal complexity of the algorithm is $O(n\times(n+e)\times b\log^2(b))$.
+
+The random tree search algorithm is probabilistically complete \cite{Lavalle2006}.
+Therefore, given enought time it will always find the optimal allocation.
+However, there is no bound on the number of sufficient iterations for finding the optimal allocation.
+We emprically demonstrate the random tree requires a very few iteration to find the equilibrium points even for very large scale graphs.

### 2016-03-15 doc/experiments.tex
updated tex file

@@
 We ensured that the graph is connected.
-The CSR game is for $m$ number of resources in the graph $G$.
+The CSR game is for $k$ number of resources in the graph $G$.
 We executed the random tree search algorithm to find the optimal allocation.
-The random tree would terminate when the cost function reaches it's maximum at $n\times m$.
+The random tree would terminate when the cost function reaches it's maximum at $n\times k$.
 For each entry point, we repeat the experiments 100 times and reported the mean number of iterations and execition time.
@@
 
-Table \ref{tab:result1} shows the result of the random tree search algorithm for different games.
-Our algorithm quickly found the equilibrium point in all of our experiments.
+%untrivila result No.1
+%when we increase the graph size for a fixed p, at the begining the problem gets harder and harder, but after a threshold point (n\p) the problem becomes a lot easier
 
-\begin{table}[]
-\centering
-\caption{Random tree search profile for different random graphs}
-\label{tab:result1}
-\begin{tabular}{lllll}
-n   & p    & m  & iterations & time (s) \\
-100 & 0.05 & 5  & 1453       & x        \\
-100 & 0.05 & 20 & 6028       & x        \\
-20  & 0.05 & 3  & 560        & x        \\
-20  & 0.5  & 10 & 1045       & x
-\end{tabular}
-\end{table}
+The hardest example would occur in sparse graphs where $n\times p << k$, where $n$ is the number of players, $k$ is number of resources and $p$ is probability of existence of an edge between two player.
+$n\times p$ is the expected number of edges between two player.
+When the expected number of edges is far smaller than the number of resources, the radius of each player substantially increases and as a result, the random tree search has to explore more space to find the optimal allocation.
 
@@
 % 2. Algorithm w.r.t. its runtime --> O(n^2)
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{result-1}
+\end{center}
+\caption{The random tree search algorithm quickly found the opimal allocation for large scale graphs.
+As we increased the number of players, the number of iterations required for finding the optimal allocation also increased.}
+\label{fig:result1}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{result-2}
+\end{center}
+\caption{As we increased the number of players, the simulation time required for finding the optimal allocation also increased. The simulation time was linearly corrolated with number of iterations.}
+\label{fig:result2}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{result-3}
+\end{center}
+\caption{When the graph was very sparse or very dense, the random tree quickly searched the state space and found the optimal allocation.
+However when the number of resources is roughtly $p\times n$, the search becames more complicated.
+The random tree stil quickly found the optimal allocation in less 4500 iterations on average.
+}
+\label{fig:result3}
+\end{figure}
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{result-4}
+\end{center}
+\caption{the runtime for the random tree algorithm is linearly corrolated with the number of iterations.
+When the graph was very sparse or very dense, the random tree quickly searched the state space and found the optimal allocation.
+However when the number of resources is roughtly $p\times n$, the search becames more complicated.
+The random tree stil quickly found the optimal allocation in less than 3 minutes.}
+\label{fig:result4}
+\end{figure}

### 2016-03-15 doc/experiments.tex
updated results

@@
 
-%untrivila result No.1
-%when we increase the graph size for a fixed p, at the begining the problem gets harder and harder, but after a threshold point (n\p) the problem becomes a lot easier
-
-The hardest example would occur in sparse graphs where $n\times p << k$, where $n$ is the number of players, $k$ is number of resources and $p$ is probability of existence of an edge between two player.
-$n\times p$ is the expected number of edges between two player.
-When the expected number of edges is far smaller than the number of resources, the radius of each player substantially increases and as a result, the random tree search has to explore more space to find the optimal allocation.
-
 % two types of results:
@@
 % 2. Algorithm w.r.t. its runtime --> O(n^2)
+
+\paragraph{Effects of player size on search}
+Figure~\ref{fig:result1} shows the result of our algorithm for different games with different number of players.
+We generated a game graph $G(n, 0.05)$ with $k=5$ resources.
+As we increased the number of players, the optimal allocation became harder to locate, but the random tree algorithm quickly found the optimal allocation even for a game with 100 players.
+When we increased the number of players beyound 100, the search actually became easier.
+Because in Erdos graph with $p=0.05$, after 100 player, every player is connected to an expected number of $5$ players or more.
+Since we only have 5 resources in that game, there are many equilibrium points in the game.
+The random tree algoritm converged almost instantly from 200 to up-to 1000 players.
+Figure~\ref{fig:result2} shows the simulation time, in second, required for finding the optimal allocation.
+Althought the worst-case execution time of our algorithm is $O(n\times(n+e)\times b\log^2(b))$, in practice the actual simulation time is corrolated linearly with the number of iterations in our implementation.
 
@@
 \end{figure}
+
+%non-trivila result No.1
+%when we increase the graph size for a fixed p, at the begining the problem gets harder and harder, but after a threshold point (n\p) the problem becomes a lot easier
+
+\paragraph{Effects of graph sparsity on search}
+The worst-case game occured where $n\times p == k$, where $n$ is the number of players, $k$ is number of resources and $p$ is probability of existence of an edge between two player.
+The expected number of edges between two player is $n\times p$.
+When the expected number of edges is far smaller than the number of resources, the radius of each player substantially increases.
+However the random tree has to make a fewer choices to satisfy players.
+As a result, the random tree search has to explore more space but the search will be easier.
+This can be seen in Figure~\ref{fig:result3}.
+On the other hand, when $n\times p >> k$, the search also becomes easier because every player is connected to many more players.
+As a result, the number of optimal allocations in the game increases and they become easier to find.
+In general, when the graph is too sparse the search was efficient.
+On the other hand, when the graph was too dense, there were multiple optimal solutions.
 
@@
 \end{figure}
+
+In order to understand the effect of resource size on the search algorithm complexity, we removed the dependency on the variable $p$ (probability of an edge between two players) from the Erdos Graph.
+Instead we used a randomly generated graph $K(n, e)$, where $n$ is the number of players in the graph and $e$ is the expected number of edges between two players.
+For each player $i$, we added $e$ edges between player $i$ and randomly chosen player $j$.
+We ensured that the graph was connected.
+Figure~\ref{fig:result_time_resources} shows the simulation time required for finding the optimal allocation for different random grpahs of 100 players versus for different resource sizes.
+We sat the number of expected edges equal as the number of resources in the game, because we saw eariler that would result in the worst-case execution of the algorithm.
+When the number of resource sizes is small, say 2 or 3, the random tree algorithm quickly converges toward the optimal allocation because the search space is very small.
+However, as the number of resources in the game increases, the search becomes harder.
+As shown in Figure~\ref{fig:result_time_resources} The runtime of the algorithm is linearly increases as the number of resources in the game increases.
+
+\begin{figure}[htb]
+\begin{center}
+\includegraphics[width=.4\textwidth]{result-time-resources}
+\end{center}
+\caption{The runtime of the random tree algorithm for different resource sizes.}
+\label{fig:result_time_resources}
+\end{figure}

### 2016-03-15 src/main.cpp

@@ -18,8 +18,8 @@ int main(int argc, const char * argv[]) {
     accumulator_set<double, stats<tag::variance> > acc2;
     int runs=10;
 	int playerSize = 100;
-	int graphConnectivityFactor = 3 ;
-	int resourceSize = 10;
+	int resourceSize = 19;
+    int graphConnectivityFactor = resourceSize ;
     double edgeProbability = 0.19;
     std::chrono::milliseconds duration;
     duration.zero();
@@ -27,8 +27,8 @@ int main(int argc, const char * argv[]) {
         double completionPercent = (100.0*i)/runs;
         cout << " Iteration " << i <<  " ," << completionPercent << "% completed." << endl ;
         Graph* g = new Graph();
-        //g->generateRandomGraph(playerSize, graphConnectivityFactor);
-        g->generateErdosRenyiRandomGraph(playerSize, edgeProbability);
+        g->generateRandomGraph(playerSize, graphConnectivityFactor);
+        //g->generateErdosRenyiRandomGraph(playerSize, edgeProbability);
         //cout << g->toString() << endl ;
         Search* search = new Search(playerSize, resourceSize, g);
         auto start = std::chrono::system_clock::now();
